---
title: "Turnover Data Cleaning"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(vegan)  
library(purrr)
library(stringr)
map <- purrr::map
select <- dplyr::select
```

This document details the various cleaning steps done to the raw BBS data. 

# Loading data

Raw data source:
https://www.pwrc.usgs.gov/BBS/RawData/

Which leads through to:

https://www.sciencebase.gov/catalog/item/52b1dfa8e4b0d9b325230cd9

Here used the 2020 release. 

## Unziping data

```{r eval = FALSE}
### Un zipping all csvs
Zipped<-list.files('../Data/2020Release_Nor/States/',pattern=".zip", full.names = TRUE, include.dirs = TRUE)
map(Zipped, function(x){unzip(x, exdir = '../Data/2020Release_Nor/Unzipped')})
```

### Combining all the seperate state csvs

```{r eval = FALSE}
AllCSVs<-list.files('../Data/2020Release_Nor/Unzipped/', full.names = TRUE)

## nb has 6.7 million rows so needs to be handled with care!
All_states_orig <- map_df(AllCSVs, read_csv,
                          col_select = c(RouteDataID ,
                                         CountryNum ,
                                         StateNum ,
                                         Route ,
                                         RPID ,
                                         Year,
                                         AOU ,
                                         StopTotal ,
                                         SpeciesTotal ),
                          col_types = cols(
                            RouteDataID = col_double(),
                            CountryNum = col_double(),
                            StateNum = col_character(),
                            Route = col_character(),
                            RPID = col_double(),
                            Year = col_double(),
                            AOU = col_character(),
                            StopTotal = col_double(),
                            SpeciesTotal = col_double()
                          ))
All_states_orig %>%
  mutate(TransectLocID = paste0('C_',CountryNum,'_S_', StateNum,'_R_', Route )) %>%
  select(TransectLocID, Year ,AOU,RPID) -> XX
 write_csv(XX, file = '../Data/2020Release_Nor/AllStates.csv')
```

```{r}
XX<- read_csv('../Data/2020Release_Nor/AllStates.csv')

IDS<- unique(XX$TransectLocID)  

weather <- read_csv( '../Data/2020Release_Nor/weather.csv') %>%
  mutate(TransectLocID = paste0('C_',CountryNum,'_S_', StateNum,'_R_', Route )) 

AllSpeciesNames <- read_csv('../Data/2020Release_Nor/SpeciesList_clean.txt', trim_ws = TRUE) %>%
  mutate(AOU = parse_number(AOU)) %>%
  select( AOU, English_Common_Name,  ORDER,Family,Genus,Species)


routes <- read_csv('../Data/2020Release_Nor/routes.csv') %>%
  mutate(TransectLocID = paste0('C_',CountryNum,'_S_', StateNum,'_R_', Route ))

```

## Removing bad surveys and tricky species

Following this advice: https://ecologicaldata.org/wiki/breeding-bird-survey-north-america

*For community analyses it is generally best to exclude nocturnal, crepuscular, and aquatic species as they are not well sampled. (That is, exclude AOU species codes <=2880 [waterbirds, shorebirds, etc], (>=3650 & <=3810) [owls], (>=3900 & <=3910) [kingfishers], (>=4160 & <=4210) [nightjars], 7010 [dipper].)*
*Surveys where RunType in the Weather table is 0 should be excluded as this indicates a survey that does not pass quality standards.*
*Only use the Run Protocol IDs (counts.RPID) that are appropriate for your study. If you just want standard BBS surveys, use RPID = 101. "Runtype = 0 indicates that the data were not collected according to prescribed methods and/or were collected during unsuitable weather conditions. "*

*StopTotal is a measure of incidence (number of point count stops out of 50 at which the species was observed), SpeciesTotal is a measure of abundance (total number of individuals across all stops)*

*Also, species taxonomy changes through time. . For example, it is not possible to retroactively assign all observations of Traill’s Flycatcher made before the species was split into the two separate species, Alder and Willow Flycatcher*

```{r}
XX %>% 
  left_join(select( weather, TransectLocID, Year, RunType ), by = c("TransectLocID", "Year")) %>%  # Join summary of routes
  filter( RunType == 1) %>% ## weather, survey type and protocol all good. (see RunType.pdf)
  mutate(AOU = parse_number(AOU)) %>% 
  left_join(AllSpeciesNames, by = "AOU") %>%
  filter(AOU > 2880) %>%  # exclude waterbirds, shorebirds, etc
  filter(AOU < 3650 | AOU > 3810) %>%  # Owls
  filter(AOU < 3900 | AOU > 3910) %>%  # Kingfishers
  filter(AOU < 4160 | AOU > 4210) %>%  #  crepuscular nightjars 
  filter(AOU != 7010) %>%              # dipper (aquatic songbird)  
  filter(ORDER != "Accipitriformes",   # hawks, eagles, vultures, and kites
         ORDER != "Falconiformes",     # falcons
         ORDER != "Anseriformes",    # waterfowl 
         ORDER != "Cathartiformes") %>% # vultures
  filter( Species != 'Sp.') %>%            # not identified to species 
  filter( !str_detect(Species, ' x ')) %>% ## remove hybrids / subsepcies (not many records)
  rename( Order = ORDER) -> FocalSpecies_df

```

## Taxonomic challenges

A moderate number of species have changed their taxonomy through time, mostly the splitting or lumping of species / subspecies. 

```{r}
FocalSpecies_df %>%
  count(AOU, Genus, Species) %>%
  mutate( Binomial = paste( Genus, Species)) %>% 
  mutate(ProblemTaxa = str_detect(Species, '/')) %>%
  filter( ProblemTaxa ) %>%
  separate(Species , into = c( 'Sp1', 'Sp2', 'Sp3'), sep = ' / ', remove = FALSE)%>%  # as.data.frame
  select( ConsolAOU = AOU,Genus,Species, Sp1,Sp2,Sp3,ProblemTaxa ) %>%
  gather( Col, Species,    Species:Sp3)  -> ProblemTaxa


FocalSpecies_df %>%
  left_join( ProblemTaxa, by = c("Genus", "Species")) %>%
  mutate( ConsolAOU = if_else(is.na(ConsolAOU), AOU, ConsolAOU ),
          ProblemTaxa = !is.na(ProblemTaxa) ) %>%
  select(TransectLocID,Year,AOU, English_Common_Name ,ConsolAOU, ProblemTaxa ) -> FocalSpecies_df_consol
```

#### Saving names for ranges
```{r}
FocalSpecies_df_consol %>%
  distinct(  AOU ,English_Common_Name,ConsolAOU ,ProblemTaxa) %>%
  write_csv('../Data/Consol_SpeciesNames.csv')
```


## Building presence / Absence matrix

Takes about 30 minutes (pivot_wider is not very fast)

```{r eval = FALSE}
## Combine the problem taxa (also removes what might be occasional duplicate surveys  eg id = 'C_840_S_02_R_141')
FocalSpecies_df_consol %>%
  distinct(TransectLocID, Year ,ConsolAOU)%>%
  group_by(TransectLocID) %>%
  nest()  -> CompactData_df_nest


matrix_form<-map(1:nrow(CompactData_df_nest),
                 function(id, alldata){
                   cat(id)
                   gc()
                   alldata$data[[id]]%>%
                     mutate( Present =1) %>%
                     pivot_wider(id_cols = Year,
                                 names_from = ConsolAOU,
                                 values_from = Present ,
                                 values_fill = 0)%>%
                     as.matrix()%>%
                     return()
                 }, CompactData_df_nest ) 

names(matrix_form) <- CompactData_df_nest$TransectLocID
save(matrix_form, file = '../Data/2020Release_Nor/matrix_form_filt1')
```

# Session info
```{r}
sessionInfo()

```







