---
title: "Linear Sim Decline Fitting"
output: html_document
date: '2022-10-13'
editor_options: 
  chunk_output_type: console
---

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(brms)
library(posterior)
map <- purrr::map
select <- dplyr::select
Average_Curves <- read_csv('../Data/All_Average_Curves.csv')

STATS_select_scaled <- read_csv('../Data/STATS_select_SCALED.csv')
BCRsToFit     <- read_csv('../Data/BCRsToFit.csv')

```

This document fits linear models through the initial rate of similarity decline (ΔS). NB - looking at decay rates, so be careful of flipping the sign of slope. It then fits the wider meta-analysis across all the BCRs.

```{r}

### Just take up to 8 years of time difference and fit an LM through
## Only BCRs with 25 

Average_Curves %>%
  filter( x<=8) %>%
  left_join(STATS_select_scaled, by = "TransectID") %>%
  filter(BCR %in% BCRsToFit$BCR) %>%
  mutate(LMWeight = 1/(0.0219^2)) %>%
  filter(!is.na(Gamma_scaled) )-> InitialDecay_all
  

TransectsToFit <- unique(InitialDecay_all$TransectID)

map_df(TransectsToFit,
       function(Transect, InitialDecay_all){
         data = filter(InitialDecay_all, TransectID == Transect)
         LM <- lm(data=data, y~x, weights=LMWeight)
         Trend <- LM$coefficients[2]
         R2 <- summary(LM)$r.squared
         SE_trend =   sqrt(diag(vcov(LM)))[2] # calculate standard error of estimate
         return(data.frame(Trend = -Trend,  #### NB sign flipping
                           SE_trend=SE_trend,
                           R2 =R2,
                           TransectID = Transect))
       },InitialDecay_all) -> InitialDecay_df
     


write_csv(InitialDecay_df, '../ModelSummaries/InitialDecay_df.csv')
```



```{r}
InitialDecay_df<- read_csv('../ModelSummaries/InitialDecay_df.csv')

InitialDecay_df %>%
  filter( Trend >0) %>%
  ggplot(aes(Trend))+
  geom_histogram()

InitialDecay_df %>%
  ggplot(aes(x=Trend, y = log10(SE_trend)))+
  geom_point()

InitialDecay_all %>%
  filter(TransectID == 'C_840_S_91_R_304') %>%
  ggplot(aes( x = x, y = y))+
  geom_point()



```

# Within-BCR Linear Models

## Fitting linear models 

```{r eval = FALSE}

InitialDecay_df %>%
  left_join(STATS_select_scaled , by = "TransectID") %>%
  as_tibble() %>%
  filter( !is.na(Gamma_Div_Ebird)) %>%
  mutate( TrendWeight = 1/(SE_trend^2))-> InitialDecay_df_stats


BCRs <- unique(InitialDecay_df_stats$BCR)

AllBCRs_Seperate_InitSlop<-map_df(BCRs, function(BCR_i){
  InitialDecay_df_stats %>%
    filter(BCR==BCR_i) -> filtdata

    lm(data = filtdata,
       Trend ~ Year_span_scaled +AvRich_100  + Av_HMindex +CV_gpp_scaled  +Gamma_scaled,
       weights = TrendWeight ) -> LM_fit 
  
  Coefs<-      as.data.frame(t(as.matrix(coefficients(LM_fit)))) 
  SEs <-           as.data.frame(t(as.matrix(  sqrt(diag(vcov(LM_fit))))))
  colnames(Coefs)<- paste0('Coefs',colnames(SEs))
  colnames(SEs)<- paste0('SE_',colnames(SEs))
  
  Coefs$R2 = summary(LM_fit)$r.squared
  Coefs$adjR2 = summary(LM_fit)$adj.r.squared
 Coefs$n = length(LM_fit$residuals)

  bind_cols(Coefs, SEs) %>%
    mutate(BCR = BCR_i) %>%
    return()
})

write_csv(AllBCRs_Seperate_InitSlop, '../ModelSummaries/AllBCRs_Seperate_InitSlopLM.csv' )
```

```{r}
AllBCRs_Seperate_InitSlop <- read_csv('../ModelSummaries/AllBCRs_Seperate_InitSlopLM.csv' )
```

# Overall 'Meta-analysis'

```{r eval = FALSE}
InitSlop_Overall_YS <- brm(bf(CoefsYear_span_scaled    |se(SE_Year_span_scaled)    ~1),
                              data = AllBCRs_Seperate_InitSlop,  silent = 2, refresh =0 )
InitSlop_Overall_HM    <- brm(bf(CoefsAv_HMindex   |se(SE_Av_HMindex )  ~1),
                              data = AllBCRs_Seperate_InitSlop, silent = 2, refresh =0 )
InitSlop_Overall_CV    <- brm(bf(CoefsCV_gpp_scaled|se(SE_CV_gpp_scaled)~1),
                              data = AllBCRs_Seperate_InitSlop , silent = 2, refresh =0)
InitSlop_Overall_AL    <- brm(bf( CoefsAvRich_100  |se(SE_AvRich_100 )  ~1),
                              data = AllBCRs_Seperate_InitSlop , silent = 2, refresh =0)
InitSlop_Overall_GM    <- brm(bf(CoefsGamma_scaled |se(SE_Gamma_scaled) ~1),
                              data = AllBCRs_Seperate_InitSlop , silent = 2, refresh =0)

bind_rows(summarise_draws(InitSlop_Overall_YS) %>% mutate( Predictor = 'YearSpan'),
          summarise_draws(InitSlop_Overall_HM) %>% mutate( Predictor = 'Humans'),
          summarise_draws(InitSlop_Overall_CV) %>% mutate( Predictor = 'CV'),
          summarise_draws(InitSlop_Overall_AL) %>% mutate( Predictor = 'Alpha'),
          summarise_draws(InitSlop_Overall_GM) %>% mutate( Predictor = 'Gamma')) -> InitSlop_Overall_Results

write_csv(InitSlop_Overall_Results, '../ModelSummaries/InitSlop_Overall_Results.csv')
```

## Quick Plot 

```{r}
InitSlop_Overall_Results <- read_csv('../ModelSummaries/InitSlop_Overall_Results.csv')

InitSlop_Overall_Results%>%
  filter(variable         =='b_Intercept')%>%
  ggplot( aes( x = Predictor))+
  geom_pointrange(aes(y = mean, ymin = q5, ymax = q95))+
  scale_colour_viridis_c()+
    geom_hline(yintercept =0)+
  ggtitle('Overall (Cross-BCR) Slope of Richness predictors')+
  coord_flip()
          
```



```{r}
AllBCRs_Seperate_InitSlop<-## read_csv('../ModelSummaries/Richness_AllBCRs_SeperateLM.csv' ) %>%
  
  AllBCRs_Seperate_InitSlop %>%
  filter(n>=25)  ### Take out BCRs that don't have at least 25 transects

Coefs<-  pivot_longer(AllBCRs_Seperate_InitSlop, names_to = 'Predictor',cols =  starts_with('Coefs'),
                values_to = 'Coefs', names_prefix = 'Coefs') %>%
    select( BCR, Predictor, Coefs)

SEs<-  pivot_longer(AllBCRs_Seperate_InitSlop, names_to = 'Predictor',cols =  starts_with('SE_'),
                values_to = 'SE', names_prefix = 'SE_') %>%
    select( BCR, Predictor, SE) 
  
left_join(Coefs, SEs, by = c("BCR", "Predictor")) %>%
  filter(Predictor != '(Intercept)')%>%
  mutate(Response = 'RichTrend')  -> InitSlope_BCR_forplot

InitSlope_BCR_forplot  %>%
  ggplot( aes( x = factor(BCR)))+
  geom_pointrange(aes(y = Coefs, ymin = Coefs+2*SE, ymax = Coefs-2*SE))+
  facet_wrap(~Predictor, scales = 'free',nrow=1)+
  geom_hline(yintercept =0)+
  theme_minimal()+
  theme(axis.title = element_blank(),
        axis.text.x = element_text(size = 5, angle = 90))

```

# Comparing Sim and Sor Dissimilarity Slopes

```{R}
Average_Curves_SIM <- read_csv('../Data/All_Average_Curves_3.csv')
```

```{r}
Average_Curves_SIM %>%
  filter( x<=8) %>%
  left_join(STATS_select_scaled, by = "TransectID") %>%
  filter(BCR %in% BCRsToFit$BCR) %>%
  mutate(LMWeight = 1/(0.0219^2)) %>%
  filter(!is.na(Gamma_scaled) )-> InitialDecay_all_SIM
  
TransectsToFit <- unique(InitialDecay_all_SIM$TransectID)

map_df(TransectsToFit,
       function(Transect, InitialDecay_all_SIM){
         data = filter(InitialDecay_all_SIM, TransectID == Transect)
         LM <- lm(data=data, y~x, weights=LMWeight)
         Trend <- LM$coefficients[2]
         R2 <- summary(LM)$r.squared
         SE_trend =   sqrt(diag(vcov(LM)))[2] # calculate standard error of estimate
         return(data.frame(Trend = -Trend,  #### NB sign flipping
                           SE_trend=SE_trend,
                           R2 =R2,
                           TransectID = Transect))
       },InitialDecay_all_SIM) -> InitialDecay_df_SIM
     
write_csv(InitialDecay_df_SIM, '../ModelSummaries/InitialDecay_df_SIM.csv')
```

```{r}
InitialDecay_df_SIM <- read_csv('../ModelSummaries/InitialDecay_df_SIM.csv')

InitialDecay_df_SIM %>%
  filter( Trend >0) %>%
  ggplot(aes(Trend))+
  geom_histogram()

InitialDecay_df_SIM %>%
  select( SIM_Trend = Trend, TransectID) %>%
  left_join(InitialDecay_df) %>%
  ggplot( aes(  SIM_Trend, Trend))+
  geom_point(alpha = 0.1)

```

## Re-Running Analysis with SIM

```{R eval = FALSE}
InitialDecay_df_SIM %>%
  left_join(STATS_select_scaled , by = "TransectID") %>%
  as_tibble() %>%
  filter( !is.na(Gamma_Div_Ebird)) %>%
  mutate( TrendWeight = 1/(SE_trend^2))-> InitialDecay_df_stats_SIM


BCRs <- unique(InitialDecay_df_stats_SIM$BCR)

AllBCRs_Seperate_InitSlop_SIM<-map_df(BCRs, function(BCR_i){
  InitialDecay_df_stats_SIM %>%
    filter(BCR==BCR_i) -> filtdata

    lm(data = filtdata,
       Trend ~ Year_span_scaled +AvRich_100  + Av_HMindex +CV_gpp_scaled  +Gamma_scaled,
       weights = TrendWeight ) -> LM_fit 
  
  Coefs<-      as.data.frame(t(as.matrix(coefficients(LM_fit)))) 
  SEs <-           as.data.frame(t(as.matrix(  sqrt(diag(vcov(LM_fit))))))
  colnames(Coefs)<- paste0('Coefs',colnames(SEs))
  colnames(SEs)<- paste0('SE_',colnames(SEs))
  
  Coefs$R2 = summary(LM_fit)$r.squared
  Coefs$adjR2 = summary(LM_fit)$adj.r.squared
 Coefs$n = length(LM_fit$residuals)

  bind_cols(Coefs, SEs) %>%
    mutate(BCR = BCR_i) %>%
    return()
})

write_csv(AllBCRs_Seperate_InitSlop_SIM, '../ModelSummaries/AllBCRs_Seperate_InitSlopLM_SIM.csv' )
```

```{r}
AllBCRs_Seperate_InitSlop_SIM <- read_csv('../ModelSummaries/AllBCRs_Seperate_InitSlopLM_SIM.csv' )
```

# Overall 'Meta-analysis' with SIM

```{r eval = FALSE}
InitSlop_Overall_YS_SIM <- brm(bf(CoefsYear_span_scaled    |se(SE_Year_span_scaled)    ~1),
                              data = AllBCRs_Seperate_InitSlop_SIM,  silent = 2, refresh =0 )
InitSlop_Overall_HM_SIM    <- brm(bf(CoefsAv_HMindex   |se(SE_Av_HMindex )  ~1),
                              data = AllBCRs_Seperate_InitSlop_SIM, silent = 2, refresh =0 )
InitSlop_Overall_CV_SIM    <- brm(bf(CoefsCV_gpp_scaled|se(SE_CV_gpp_scaled)~1),
                              data = AllBCRs_Seperate_InitSlop_SIM , silent = 2, refresh =0)
InitSlop_Overall_AL_SIM    <- brm(bf( CoefsAvRich_100  |se(SE_AvRich_100 )  ~1),
                              data = AllBCRs_Seperate_InitSlop_SIM , silent = 2, refresh =0)
InitSlop_Overall_GM_SIM    <- brm(bf(CoefsGamma_scaled |se(SE_Gamma_scaled) ~1),
                              data = AllBCRs_Seperate_InitSlop_SIM , silent = 2, refresh =0)

bind_rows(summarise_draws(InitSlop_Overall_YS_SIM) %>% mutate( Predictor = 'YearSpan'),
          summarise_draws(InitSlop_Overall_HM_SIM) %>% mutate( Predictor = 'Humans'),
          summarise_draws(InitSlop_Overall_CV_SIM) %>% mutate( Predictor = 'CV'),
          summarise_draws(InitSlop_Overall_AL_SIM) %>% mutate( Predictor = 'Alpha'),
          summarise_draws(InitSlop_Overall_GM_SIM) %>% mutate( Predictor = 'Gamma')) -> InitSlop_Overall_Results_SIM

write_csv(InitSlop_Overall_Results_SIM, '../ModelSummaries/InitSlop_Overall_Results_SIM.csv')

```

## Comparison

```{r}
InitSlop_Overall_Results_SIM <- read_csv('../ModelSummaries/InitSlop_Overall_Results_SIM.csv')
InitSlop_Overall_Results <- read_csv('../ModelSummaries/InitSlop_Overall_Results.csv')

dodge <- position_dodge(width=0.5)  

bind_rows(InitSlop_Overall_Results%>%
            filter(variable         =='b_Intercept')%>%
            select( Predictor, mean, q5, q95) %>%
            mutate( Measure = 'SOR') , 
          InitSlop_Overall_Results_SIM%>%
            filter(variable         =='b_Intercept')%>%
            select( Predictor, mean, q5, q95) %>%
            mutate( Measure = 'SIM') ) %>%
  ggplot( aes( x = Predictor, col = Measure),position=dodge)+
  geom_pointrange(aes(y = mean, ymin = q5, ymax = q95),position=dodge)+
  geom_hline(yintercept =0)+
  ggtitle('Overall (Cross-BCR) Short-term Turnover (ΔS) predictors')+
  theme_minimal()


## NB combined with others in Final Analysis doc
```



```{r}
sessionInfo()
```








