---
title: "Final Output of Figures"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

This document collates the results calculated in other scripts to make the bulk of the final figures for the MS.

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(vegan)  
library(purrr)
library(brms)
library(stringr)
library(bayesplot)
library(tidybayes)
library(posterior)
library(cowplot)
library(scales)


map <- purrr::map
select <- dplyr::select

logit <- function(x){return(log(x/(1-x)))}
inv_logit <- function(x){exp(x)/(1+exp(x))}


read_csv('../Data/All_Average_Curves.csv')%>%
  left_join(read_csv('../Data/STATS_select_SCALED.csv'), by = "TransectID") %>%
  filter( !is.na(Gamma_Div_Ebird))-> UnCenteredData

STATS <- read_csv('../Data/STATS.csv')
STATS_select <- read_csv('../Data/STATS_select.csv')
STATS_select_scaled <- read_csv('../Data/STATS_select_SCALED.csv')

RichnessSlope_df <- read_csv('../ModelSummaries/RichnessSlope_df.csv')

STR_fit_df <- read_csv('../ModelSummaries/STR_AllBCRs_Seperate.csv')
STR <- read_csv('../ModelFits/STR_fitsdf.csv')

InitialDecay_df<- read_csv('../ModelSummaries/InitialDecay_df.csv')
InitSlop_fit   <- read_csv('../ModelSummaries/InitSlop_Overall_Results.csv')

## Loading fits 
SummaryTableRE_Human  <- read_csv('../ModelSummaries/SummaryTable_ALL3.csv')
AllInferredCurveParams<- read_csv('../ModelSummaries/AllCurveParams_WOPreds1.csv') # made elsewhere

AllCurveCoefs<- read_csv('../ModelSummaries/AllCurveCoefs.csv')
Inferred_UnCertainty <- read_csv('../ModelSummaries/Inferred_UnCertaintyDL.csv')



```

# Main Results - Figure 4 

## Left side - histograms of parameters
```{r}

DF<-AllInferredCurveParams %>%
  left_join(RichnessSlope_df, by = "TransectID") %>%
  left_join(select(STR, TransectID, LogLog_z), by = "TransectID") %>%
  left_join(select(InitialDecay_df, TransectID, InitialDecay=Trend ), by = "TransectID")

Histogram_theme <- theme_minimal()+theme(axis.title = element_blank())

Hist_Richness<-   ggplot(DF, aes( x= Trend))+
  geom_histogram(bins = 100)+Histogram_theme+
  ggtitle('e) ΔR Species Richness Trend')+
  theme(axis.text.y = element_blank())

Hist_Accum<-   ggplot(DF, aes( x= LogLog_z))+
  geom_histogram(bins = 100)+Histogram_theme +
  ggtitle('f) z Species Accumulation Exponent')+
  theme(axis.text.y = element_blank())


Hist_Decay <-   DF %>%
  filter( InitialDecay >-0.02) %>%
  ggplot(aes( x=InitialDecay ))+
  geom_histogram(bins = 100)+Histogram_theme +
  ggtitle('d) ΔS Initial Similarity Decay')+
  theme(axis.text.y = element_blank())

Hist_Omega<-   ggplot(DF, aes( x= InferredO))+
  geom_histogram(bins = 100)+Histogram_theme+
  ggtitle('a) ω Observation Repeatability') +
  theme(axis.text.y = element_blank())

Hist_L<-  ggplot(DF, aes( x= 
                       InferredL))+ 
  geom_histogram(bins = 100)+Histogram_theme+
  scale_x_log10()+
  ggtitle('c) L Similarity Decay Rate')+
  theme(axis.text.y = element_blank())

Hist_d<- ggplot(DF, aes( x= InferredD))+
  geom_histogram(bins = 100)+Histogram_theme+
  ggtitle('b) d Asymptopic Similarity')+
  theme(axis.text.y = element_blank())
```

## Right-Side - Posteriors of predictors on turnover component

```{r}
x_scale_labels <-  c('Human\nImpact' ,
                              'Env.\nVariability', 
                              'Species\nRichness',
                              'Species\nPool', 
                              'Year\nSpan')

right_rich <- read_csv('../ModelSummaries/Richness_Overall_Results.csv')%>%
  filter(variable=='b_Intercept')%>%
  mutate(P2 = recode(Predictor,
                     'Humans'='Human\nImpact' ,
                     'CV'  ='Env.\nVariability', 
                     'Alpha'  ='Species\nRichness',
                     'Gamma' ='Species\nPool', 
                     'YearSpan' = 'Year\nSpan')) %>%
  ggplot( aes( x = P2))+
    geom_point(aes(y = mean))+
  geom_linerange(aes(ymin = q5, ymax = q95), col = 'grey10')+
  geom_hline(yintercept =0)+
  theme(panel.grid.major.x = element_blank())+
  ggtitle('')+ theme_minimal()+ ylab('')+xlab('')+
  scale_x_discrete(limits =x_scale_labels)


right_str <- read_csv('../ModelSummaries/STR_Overall_Results.csv')%>%
  filter(variable=='b_Intercept')%>%
  mutate(P2 = recode(Predictor,
                     'Humans'='Human\nImpact' ,
                     'CV'  ='Env.\nVariability', 
                     'Alpha'  ='Species\nRichness',
                     'Gamma' ='Species\nPool', 
                     'YearSpan' = 'Year\nSpan')) %>%
  ggplot( aes( x = P2))+
    geom_point(aes(y = mean))+
  geom_linerange(aes(ymin = q5, ymax = q95), col = 'grey10')+
  geom_hline(yintercept =0)+
  theme(panel.grid.major.x = element_blank())+
  ggtitle('')+
  theme_minimal()+ ylab('')+xlab('')+
  scale_x_discrete(limits = x_scale_labels)

right_Slop <- read_csv('../ModelSummaries/InitSlop_Overall_Results.csv')%>%
  filter(variable=='b_Intercept')%>%
  mutate(P2 = recode(Predictor,
                     'Humans'='Human\nImpact' ,
                     'CV'  ='Env.\nVariability', 
                     'Alpha'  ='Species\nRichness',
                     'Gamma' ='Species\nPool', 
                     'YearSpan' = 'Year\nSpan')) %>%
  ggplot( aes( x = P2))+
    geom_point(aes(y = mean))+
  geom_linerange(aes(ymin = q5, ymax = q95), col = 'grey10')+
  geom_hline(yintercept =0)+
  theme(panel.grid.major.x = element_blank())+
  ggtitle('')+
  theme_minimal()+ ylab('')+xlab('')+
  scale_x_discrete(limits = x_scale_labels)

AllCurveCoefs%>%
  mutate( P2 = recode(Predictor,
                      'HM'='Human\nImpact' ,
                      'CV'  ='Env.\nVariability', 
                      'AL'  ='Species\nRichness',
                      'GM' ='Species\nPool',
                      'YS' = 'Year\nSpan')) -> AllCurveCoefs2

right_omeg<- ggplot(  filter(AllCurveCoefs2, Response =='o'), aes( x = P2))+
    geom_point(aes(y = mean))+
  geom_linerange(aes(ymin = q5, ymax = q95), col = 'grey10')+
  geom_hline(yintercept =0)+
  ggtitle('')+ theme_minimal()+ ylab('')+xlab('')+
  theme(panel.grid.major.x = element_blank())+
  scale_x_discrete(limits = x_scale_labels)

right_L<- ggplot(  filter(AllCurveCoefs2, Response =='L'), aes( x = P2))+
    geom_point(aes(y = mean))+
  geom_linerange(aes(ymin = q5, ymax = q95), col = 'grey10')+
  geom_hline(yintercept =0)+
  ggtitle('')+ theme_minimal()+ ylab('')+xlab('')+
  theme(panel.grid.major.x = element_blank())+
  scale_x_discrete(limits = x_scale_labels)

right_d<- ggplot(  filter(AllCurveCoefs2, Response =='d'), aes( x = P2))+
    geom_point(aes(y = mean))+
  geom_linerange(aes(ymin = q5, ymax = q95), col = 'grey10')+
  geom_hline(yintercept =0)+
  ggtitle('')+ theme_minimal()+ ylab('')+xlab('')+
  theme(panel.grid.major.x = element_blank())+
  scale_x_discrete(limits = x_scale_labels)
```

## Complete plot

```{r}
plot_grid( 
  plot_grid(Hist_Omega,Hist_d,Hist_L, ncol=1),
  plot_grid(right_omeg, right_d,right_L,ncol = 1),
  plot_grid(Hist_Decay,Hist_Richness,Hist_Accum, ncol=1),
  plot_grid(right_Slop, right_rich,right_str,
            ncol = 1),
  rel_widths = c(2,4,2,4), ncol = 4
)-> MainResults

MainResults

ggsave( '../MS_figs/MainResults.png', plot = MainResults,
        height = 8, width = 12, bg = "white", dpi = 100)

ggsave( '../MS_figs/MainResults_HiRES.png', plot = MainResults,
        height = 8, width = 12, bg = "white", dpi = 600)

```
# Results split by BCR - SI 2

```{r}
### Similarity Decay

SummaryTableRE_Human%>% 
  filter(str_detect(variable, 'beta'))%>%
  mutate(Response = str_sub(variable,7,7),
         Predictor = str_sub(variable,8,9)) %>%
  select( Coefs =mean,SE = sd, BCR, Response, Predictor)-> SimDecay_BCR_forplot

### STR by BCR (NB 2x SE, not 90%)
AllBCRs_Seperate_STR <- read_csv('../ModelSummaries/STR_AllBCRs_SeperateLM.csv' )

Coefs<-  pivot_longer(AllBCRs_Seperate_STR, names_to = 'Predictor',cols =  starts_with('Coefs'),
                values_to = 'Coefs', names_prefix = 'Coefs') %>%
    select( BCR, Predictor, Coefs)

SEs<-  pivot_longer(AllBCRs_Seperate_STR, names_to = 'Predictor',cols =  starts_with('SE_'),
                values_to = 'SE', names_prefix = 'SE_') %>%
    select( BCR, Predictor, SE)  
  
left_join(Coefs, SEs, by = c("BCR", "Predictor")) %>%
  filter(Predictor != '(Intercept)')%>%
  mutate(Response= 'z')-> STR_BCR_forplot
  
### Richness Trends by BCR  

AllBCRs_Seperate_Richness<- read_csv('../ModelSummaries/Richness_AllBCRs_SeperateLM.csv' ) %>%
  filter(n>=25)  ### Take out BCRs that don't have at least 25 transects

Coefs<-  pivot_longer(AllBCRs_Seperate_Richness, names_to = 'Predictor',cols =  starts_with('Coefs'),
                values_to = 'Coefs', names_prefix = 'Coefs') %>%
    select( BCR, Predictor, Coefs)

SEs<-  pivot_longer(AllBCRs_Seperate_Richness, names_to = 'Predictor',cols =  starts_with('SE_'),
                values_to = 'SE', names_prefix = 'SE_') %>%
    select( BCR, Predictor, SE) 
  
left_join(Coefs, SEs, by = c("BCR", "Predictor")) %>%
  filter(Predictor != '(Intercept)')%>%
  mutate(Response = 'RichTrend')  -> Richness_BCR_forplot

### Initial Slope

AllBCRs_Seperate_InitSlop <- read_csv('../ModelSummaries/AllBCRs_Seperate_InitSlopLM.csv')

Coefs<-  pivot_longer(AllBCRs_Seperate_InitSlop, names_to = 'Predictor',cols =  starts_with('Coefs'),
                values_to = 'Coefs', names_prefix = 'Coefs') %>%
    select( BCR, Predictor, Coefs)

SEs<-  pivot_longer(AllBCRs_Seperate_InitSlop, names_to = 'Predictor',cols =  starts_with('SE_'),
                values_to = 'SE', names_prefix = 'SE_') %>%
    select( BCR, Predictor, SE) 
  
left_join(Coefs, SEs, by = c("BCR", "Predictor")) %>%
  filter(Predictor != '(Intercept)')%>%
  mutate(Response = 'InitSlope')  -> InitSlope_BCR_forplot

## joining all Together

bind_rows(SimDecay_BCR_forplot,
          STR_BCR_forplot,
          Richness_BCR_forplot,
          InitSlope_BCR_forplot) %>%
  mutate(P2 = recode(Predictor,
                     'HM'='Human Impact' ,
                     'CV'  ='Variability', 
                     'AL'  ='Species Richness',
                     'GM' ='Species Pool', 
                     'YS' = 'Year Span',
                     'Av_HMindex'='Human Impact' ,
                     'CV_gpp_scaled'  ='Variability', 
                     'AvRich_100'  ='Species Richness',
                     'Gamma_scaled' ='Species Pool', 
                     'N_years50' = 'Year Span',
                     'Year_span50' = 'Year Span',
                     'Year_span_scaled' = 'Year Span'),
         R2 = recode(Response,
                     'd'='d (Asymptopic Similarity))' ,
                     'L'  ='L (Similarity Decay Timescale)', 
                     'o'  ='ω (Observation Repeatability)',
                     'RichTrend' ='ΔR (Trend In Species Richness)', 
                     'z' = 'z (Species Accumulation Exponent)',
                     'InitSlope' = 'ΔS (Initial Slope)'))-> AllResponses_BCR_forplot
```

```{r}

A<- AllResponses_BCR_forplot  %>%
  filter( Response =='o') %>%
  ggplot( aes( x = factor(BCR)))+
  geom_pointrange(aes(y = Coefs, ymin = Coefs+2*SE, ymax = Coefs-2*SE))+
  facet_wrap(~P2, scales = 'free',nrow=1)+
  geom_hline(yintercept =0)+
  theme_minimal()+
  theme(axis.title = element_blank(),
        axis.text.x = element_text(size = 5, angle = 90))+
  ggtitle('a) ω (Observation Repeatability)')

B<- AllResponses_BCR_forplot  %>%
  filter( Response =='d') %>%
  ggplot( aes( x = factor(BCR)))+
  geom_pointrange(aes(y = Coefs, ymin = Coefs+2*SE, ymax = Coefs-2*SE))+
  facet_wrap(~P2, scales = 'free',nrow=1)+
  geom_hline(yintercept =0)+
  theme_minimal()+
  theme(axis.title = element_blank(),
        axis.text.x = element_text(size = 5, angle = 90))+
  ggtitle('b) d (Asymptopic Similarity)' )

C<- AllResponses_BCR_forplot  %>%
  filter( Response =='L') %>%
  ggplot( aes( x = factor(BCR)))+
  geom_pointrange(aes(y = Coefs, ymin = Coefs+2*SE, ymax = Coefs-2*SE))+
  facet_wrap(~P2, scales = 'free',nrow=1)+
  geom_hline(yintercept =0)+
  theme_minimal()+
  theme(axis.title = element_blank(),
        axis.text.x = element_text(size = 5, angle = 90))+
  ggtitle('c) L (Similarity Decay Rate)')

D<- AllResponses_BCR_forplot  %>%
  filter( Response =='InitSlope') %>%
  ggplot( aes( x = factor(BCR)))+
  geom_pointrange(aes(y = Coefs, ymin = Coefs+2*SE, ymax = Coefs-2*SE))+
  facet_wrap(~P2, scales = 'free',nrow=1)+
  geom_hline(yintercept =0)+
  theme_minimal()+
  theme(axis.title = element_blank(),
        axis.text.x = element_text(size = 5, angle = 90))+
  ggtitle('d) ΔS (Initial Slope)' )

E<- AllResponses_BCR_forplot  %>%
  filter( Response =='RichTrend') %>%
  ggplot( aes( x = factor(BCR)))+
  geom_pointrange(aes(y = Coefs, ymin = Coefs+2*SE, ymax = Coefs-2*SE))+
  facet_wrap(~P2, scales = 'free',nrow=1)+
  geom_hline(yintercept =0)+
  theme_minimal()+
  theme(axis.title = element_blank(),
        axis.text.x = element_text(size = 5, angle = 90))+
  ggtitle('e) ΔR (Trend In Species Richness)')

F.<- AllResponses_BCR_forplot  %>%
  filter( Response =='z') %>%
  ggplot( aes( x = factor(BCR)))+
  geom_pointrange(aes(y = Coefs, ymin = Coefs+2*SE, ymax = Coefs-2*SE))+
  facet_wrap(~P2, scales = 'free',nrow=1)+
  geom_hline(yintercept =0)+
  theme_minimal()+
  theme(axis.title = element_blank(),
        axis.text.x = element_text(size = 5, angle = 90))+
  ggtitle( 'f) z (Species Accumulation Exponent)')


ALL_BCR_SIResults <-plot_grid(A,B, C, D, E,F., ncol=1)

ggsave( '../MS_figs/SI2_BCR_level_results.png',
        ALL_BCR_SIResults,
        height = 18, width = 12, bg = 'white')


```

# Other Plots and Data Summmaries

## Basic Stats of Transects

```{r}
AllInferredCurveParams %>%
  left_join(STATS, by = c("BCR", "TransectID")) %>%
  summarise(N_Transects = n(),
            Av_N_Surveys = mean(N_Surveys),
            Av_N_YearSpan = mean(Year_span), 
            sd_N_Surveys = sd(N_Surveys),
            sd_N_YearSpan = sd(Year_span)
  )
```

### Correlation in predictor variables (SI 1B)

```{r}
UnCenteredData %>%
  select('Human\nImpact'=Av_HMindex,
         'Variability'=  CV_gpp_scaled,
         'Species\nPool'= Gamma_Div_Ebird ,
         'Species\nRichness' = Average_Richness,
         'Year\nSpan'=Year_span,
         BCR, TransectID)  %>%
  distinct() %>%
  filter(TransectID %in% AllInferredCurveParams$TransectID)-> CorrData

Values<- CorrData %>%pivot_longer(1:5,
               names_to="x_var", values_to="x_val")
Values2 <- rename(Values, y_var = x_var, y_val = x_val)

full_join(Values, Values2, by = c("TransectID", "BCR")) %>%
  select(-TransectID) %>%
  filter( x_var != y_var) %>%
  nest(data=c(x_val, y_val)) %>%
  mutate(cor = map_dbl(data, ~cor(.x$x_val, .x$y_val, method = 'pearson'))) %>%
  group_by(x_var,y_var    ) %>%
  summarise( mean_cor = mean(cor),
             sd_cor = sd(cor)) -> Average_Within_BCR_Corrs

full_join(Values, Values2, by = c("TransectID", "BCR")) %>%
  select(-TransectID, -BCR) %>%
  filter( x_var != y_var) %>%
    nest(data=c(x_val, y_val)) %>%
  mutate(cor = map_dbl(data, ~cor(.x$x_val, .x$y_val, method = 'pearson'))) %>%
  select(-data) -> Overall_Corrs

Overall_Corrs %>%
  ggplot(aes( x = x_var, y = y_var, fill = cor))+
  geom_tile()+
  geom_text(aes(label = paste(signif(cor,3) )))+
  scale_fill_gradient2(limits = c(-1, 1), name = 'Correlation  ')+
  ggtitle('i) Overall')+
  theme_minimal()+ coord_fixed()+
  theme(panel.grid = element_blank(),
        legend.position = 'bottom')+
  xlab('')+ylab('') -> OverallCorr

Average_Within_BCR_Corrs %>%
  ggplot(aes( x = x_var, y = y_var, fill = mean_cor))+
  geom_tile()+
  # geom_text(aes(label = paste('Mean =',signif(mean_cor,3),
  #                             '\nSD =',signif(sd_cor,3) )))+
  geom_text(aes(label = paste(signif(mean_cor,3))))+
  scale_fill_gradient2(limits = c(-1, 1), name = 'Correlation  ')+
  ggtitle('ii) Average Within-BCR')+
  theme_minimal()+ coord_fixed()+
  theme(panel.grid = element_blank(),
        legend.position = 'bottom')+
  xlab('')+ylab('') -> WithinBCRCORR


CorrelationSI_Fig <- plot_grid(OverallCorr , WithinBCRCORR)
CorrelationSI_Fig


```


### Distribution of values of predictors  (SI 1A)
```{r}
UnCenteredData %>%
  left_join(STATS) %>%
  select('i) Human Impact'=Av_HMindex,
         'ii) Environmental Variability'=  CV_gpp_scaled,
         'iii) Species Pool'= Gamma_Div_Ebird ,
         'iv) Species Richness' = Average_Richness,
         'v) Year Span'=Year_span,
         'vi) Number of Surveys on Transect' = N_Surveys,
         'vii) Number of "Permanent" Species'=N_Permanent,
         'viii) Initial Year' =StartYear,
         BCR, TransectID)  %>%
  distinct()  %>%
  filter(TransectID %in% AllInferredCurveParams$TransectID)%>%
  pivot_longer(1:8,
               names_to="x_var", values_to="x_val")%>%
  ggplot( aes( x = x_val))+
  geom_histogram(bins=20)+
  facet_wrap(~x_var, scales = 'free_x', nrow = 2)+
  theme_minimal()+xlab('')+ylab('')+
  theme(strip.text = element_text(hjust = 0))+
  ggtitle('')-> SIFig1_dist

SIFig1_dist

```

### Joining

```{r}

SIfig1 <- plot_grid( SIFig1_dist, CorrelationSI_Fig, ncol = 1,
           labels = c( 'A', 'B'))

ggsave( '../MS_figs/SI1_corrs.png',
        SIfig1,
        width = 10, height = 10, bg='white')
```

## Correlations in Fitted Values of Similarity Decay (SI 3)

```{r}
AllInferredCurveParams %>%
  left_join(Inferred_UnCertainty, by = c("BCR", "TransectID")) %>%
  arrange(InferredD) %>%
  ggplot(aes( x = InferredD,  InferredL, col = InferredD_SD ))+
  geom_point(size = 1)+
  scale_y_log10()+
  scale_colour_viridis_c(name = 'Uncertainty in d\n(SD of posterior)')+
  theme_minimal()+
  theme(legend.position = 'bottom')+
  xlab('Inferred Asymptote (d)')+
  ylab('Inferred Decay Rate (L)')

ggsave('../MS_figs/SI3_LDCorr.png', width = 5, height = 7, bg = 'white' )
```

### Impact of Year Span on uncertainty in d (Not in MS)

```{r}
SummaryTableRE_Human %>%
  filter(str_detect(variable ,pattern =  'r_TransectID__logitd0')) %>%
  select( variable, RE_term_logitd0_sd =sd      , BCR) %>% 
  mutate(TransectID  = str_sub(variable, 23,38 )) %>%
  select(-variable) %>%
  left_join(STATS_select_scaled, by = c("BCR", "TransectID")) -> UnCertaintyinD

UnCertaintyinD%>%
  ggplot(aes( x = Year_span_scaled, y=RE_term_logitd0_sd ))+
  geom_point()+
  geom_smooth()

```


# Session Info

```{r}
sessionInfo()
```

