---
title: "Cross referencing Transects and eBird range maps"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

NB route shape files and ebird distributions are not included in this repository. 

```{r warning = FALSE, message = FALSE}
library(sf)
library(tidyverse)
library(lwgeom)
library(raster)
library(ebirdst)
library(exactextractr)  # for polygon / rster intersections
library(lubridate)

map <- purrr::map
select <- dplyr::select

L48Routes<-read_sf('../Data/Lower48_routes/bbsrtsl020.shp')  # https://earthworks.stanford.edu/catalog/stanford-vy474dv5024

AllRoutes<- read_csv('../Data/2020Release_Nor/routes.csv')%>%
  mutate(RTENO = parse_number(paste0(StateNum ,Route)))
```

NB Joining transect routes and bird observations by route name is not reliable- duplicate names due to routes being split and  poor name cleanliness means matching fails too. 

The route number consists of the 1- or 2-digit State ID code followed by the 3-digit route ID. State codes are as follows: 

ID Number State


2 Alabama 
6 Arizona 
7 Arkansas 
14 California 
17 Colorado 
18 Connecticut
21 Delaware
25 Florida
27 Georgia
33 Idaho
34 Illinois
35 Indiana 
36 Iowa 
38 Kansas 
39 Kentucky 
42 Louisiana
44 Maine 
46 Maryland 
47 Massachusetts
49 Michigan
50 Minnesota
51 Mississippi 
52 Missouri 
53 Montana 
54 Nebraska 
55 Nevada 
58 New Hampshire
59 New Jersey 
60 New Mexico 
61 New York 
63 North Carolina
64 North Dakota 
66 Ohio 
67 Oklahoma
69 Oregon 
72 Pennsylvania
77 Rhode Island 
80 South Carolina
81 South Dakota
82 Tennessee
83 Texas
85 Utah
87 Vermont
88 Virginia
89 Washington
90 West Virginia
91 Wisconsin
92 Wyoming


# Species Range Maps

## Data source: eBird

Downloading the full shape files from the website https://ebird.org/science/status-and-trends/download-data

*Fink, D., T. Auer, A. Johnston, M. Strimas-Mackey, O. Robinson, S. Ligocki, W. Hochachka, C. Wood, I. Davies, M. Iliff, L. Seitz. 2020. eBird Status and Trends,  Data Version: 2019; Released: 2020 Cornell Lab of Ornithology, Ithaca, New York. https://doi.org/10.2173/ebirdst.2019*

This script assumes all range maps are stored in Downloads/all-range-2021.gpkg/  (NB very large file >8 Gb and throttled download)

*Files are named with Cornell's 6 letter code*

### Snowy egret example

An example to illustrate process in knitr markdown.


```{R message = FALSE}
### The raw package contains both range and prediction area polygons - Prediction area polygons are just well sampled areas where they try and predict the location of the species

st_layers('~/Downloads/all-range-2021.gpkg/snoegr-rangeRaw-2021.gpkg')

snoegr_raw_range <- st_read('~/Downloads/all-range-2021.gpkg/snoegr-rangeRaw-2021.gpkg', layer = 'range')

## Data is divided by season:
snoegr_raw_range %>%
  ggplot( )+
  geom_sf( aes(fill = season), )+
  facet_wrap(start_dt~season)+
  ggtitle('Raw, all seasons')+
  coord_sf(ylim = c( 25,45),
           xlim = c(-130, -60))

snoegr_raw_range %>%
    filter(season == 'breeding' ) %>%
  ggplot( )+
  geom_sf( aes(fill = season))+
  ggtitle('Raw')+
  coord_sf(ylim = c( 25,45),
           xlim = c(-130, -60))

## 
snoegr_mr_range <- st_read('~/Downloads/all-range-2021.gpkg/snoegr-range-mr-2021.gpkg', layer = 'range')

snoegr_mr_range %>%
    filter(season == 'breeding' ) %>%
  ggplot( )+
  geom_sf( aes(fill = season))+
  ggtitle('mr - medium resolution smoothing')+
  coord_sf(ylim = c( 25,45),
           xlim = c(-130, -60))

## 
snoegr_lr_range <- st_read('~/Downloads/all-range-2021.gpkg/snoegr-range-lr-2021.gpkg', layer = 'range')

snoegr_lr_range %>%
  filter(season == 'breeding' ) %>%
  ggplot( )+
  geom_sf( aes(fill = season))+
  ggtitle('lr - low resolution smoothing')+
  coord_sf(ylim = c( 25,45),
           xlim = c(-130, -60))

```

## Intersection of routes with example range

NB Original ebird CNRS = 4326, while route CNRS = 4269
 
Raw polygons take far too long to do anything useful with

```{r message = FALSE}
### First make a bounding box of the US
extent_ras <- extent(-150, -50, 20, 80)
extent_sf <- st_set_crs(st_as_sf(as(extent_ras, "SpatialPolygons")), 4269)

mr_breeding_snowegret <- filter(snoegr_mr_range, season == 'breeding' ) %>%
  st_transform(crs =4269 ) %>%
  st_crop(y = extent_sf)

InRange <- st_intersects(L48Routes$geometry,mr_breeding_snowegret$geom , sparse=FALSE) # takes 20 seconds or so for one species
L48Routes$InSnowEgretRange<- InRange[,1]

L48Routes %>%
  ggplot( )+
  geom_sf(data = mr_breeding_snowegret,
          aes(geometry = geom) , fill = 'yellow')+
  geom_sf(aes(geometry = geometry, col = InSnowEgretRange))

L48Routes %>%
  ggplot( )+
  geom_sf(data = mr_breeding_snowegret,
          aes(geometry = geom) , fill = 'yellow')+
  geom_sf(aes(geometry = geometry, col = InSnowEgretRange))+
  coord_sf(xlim = c(-91, -88), ylim = c( 35,37))+
  ggtitle('Zooming in on a particular area')
```


# Full dataset

## Testing and matching names across datasets

```{r message = FALSE, warning = FALSE}

Species_formatted<- read_csv('../Data/2020Release_Nor/Species_formatted.csv' )
Consol_SpeciesNames<- read_csv('../Data/Consol_SpeciesNames.csv' )

Consol_SpeciesNames %>%
  left_join(Species_formatted, by = c('ConsolAOU' = 'aou' ) ) %>%
  rename(PostConsol_EnglishName = english_common_name,
         PreConsol_EnglishName = English_Common_Name) %>%
  select( -spanish_common_name            , -french_common_name ) %>%
   filter(!str_starts(PreConsol_EnglishName,'unid.'),
          !str_starts(PreConsol_EnglishName,'Unid.')) %>% #######################  Take out all the species labels that are unidentifiable between species
  mutate( ebird_ID_fromBinom =get_species(paste(genus,species)))-> Species_Names


nrow(distinct(Consol_SpeciesNames, ConsolAOU))  ## dataset has 379 consolidated species names in it = i.e. lumping together species that were considered one species at some point during the survey

### For those species that were lumped, need to have them 'unlumped' for the purpose of ebird maps
## Easiest way to do that is to use the pre-consolidation english names: 

Species_Names %>%
  arrange(ConsolAOU ) %>%
  mutate( ebird_ID_fromCommon = get_species( PreConsol_EnglishName  )) -> Species_Names2



```

This leaves 21 species names in the BBS data that don't have an easy analogue in the eBird dataset. 
Partly naming is not consistent between the datasets. eBird seems to be more up-to-date. 

Still some species that should be available, but for some reason don't have trends data available in ebird. 
e.g.  Spot-breasted Oriole  *Icterus pectoralis*, is all present and correct on the ebird website, https://ebird.org/species/spbori?siteLanguage=en_GB, but does not have a trend. 

Fixing them manually where possible:

```{r}
Species_Names2 %>%
  filter(is.na(ebird_ID_fromBinom), is.na(ebird_ID_fromCommon)) %>%
  arrange(ConsolAOU ) %>% 
  as.data.frame()
```

```{r}
Species_Names2 %>%
  mutate(ebird__ID_Manual =  ifelse(PreConsol_EnglishName =='Willow Ptarmigan','wilpta', NA ),
         ebird__ID_Manual =  ifelse(PreConsol_EnglishName %in% c('(Yellow-shafted Flicker) Northern Flicker',
                                                                 '(Red-shafted Flicker) Northern Flicker'),'norfli',ebird__ID_Manual ),
         ebird__ID_Manual =  ifelse(PreConsol_EnglishName =='Spot-breasted Oriole','spbori',ebird__ID_Manual ),
         ebird__ID_Manual =  ifelse(str_detect(PreConsol_EnglishName, 'Dark-eyed Junco'),'daejun',ebird__ID_Manual ),
         ebird__ID_Manual =  ifelse(PreConsol_EnglishName =="Botteri's Sparrow",'botspa',ebird__ID_Manual ),
         ebird__ID_Manual =  ifelse(str_detect(PreConsol_EnglishName, 'Yellow-rumped Warbler'),'yerwar',ebird__ID_Manual ),
         ebird__ID_Manual =  ifelse(PreConsol_EnglishName =='Bahama Mockingbird','bahmoc',ebird__ID_Manual ),
         ebird__ID_Manual =  ifelse(PreConsol_EnglishName =='Pin-tailed Whydah ','pitwhy',ebird__ID_Manual )
         ) -> Species_Names3

Species_Names3 %>%
mutate(ebird_ID_used = ifelse(!is.na(ebird__ID_Manual ),ebird__ID_Manual,
                              ifelse(  !is.na(ebird_ID_fromCommon ) ,ebird_ID_fromCommon,ebird_ID_fromBinom))) ->Species_Names_allcodes

Ebird_Codes <- unique(Species_Names_allcodes$ebird_ID_used)

```

```{r eval = FALSE}
write_csv(Species_Names_allcodes, '../Data/Species_Names_allcodes.csv')

```


### Checking which have codes

```{r}
All_gpkg_names <- list.files('../../../Downloads/all-range-2021.gpkg/')
MR_names <-All_gpkg_names[str_detect(All_gpkg_names, 'range-mr') ]

ebird_codes_withmaps <-str_split(MR_names, '-', simplify = TRUE)[,1]

### Mostly weird species that fail
Species_Names_allcodes %>%
  filter( !(ebird_ID_used %in% ebird_codes_withmaps) )

```

## Intersection of routes with example range

```{r}
### First make a bounding box of the US
extent_ras <- extent(-150, -50, 20, 80)
extent_sf <- st_set_crs(st_as_sf(as(extent_ras, "SpatialPolygons")), 4269)

## Extracting Dates 
### just setting early june as main period of BBS surveys but nb there is some more more wiggle room in some areas

Survey_dates =interval(ymd('2020-06-01'), ymd('2020-06-10')) 

### Cycling through and loading up all the range maps

Ebird_Codes[Ebird_Codes %in% ebird_codes_withmaps] %>%
  map_df(function(ebird_code){
    
    st_read(paste0('~/Downloads/all-range-2021.gpkg/',
                   ebird_code,'-range-mr-2021.gpkg'),
            layer = 'range',  quiet = TRUE) %>%
      return()
  }) -> All_June_Range_Maps

### some annoying differences in breeding times mean can't select map to use based on breeding status
### Within each species, will take union of all maps that align with BBS survey dates         

All_June_Range_Maps_time  <-All_June_Range_Maps %>%
  mutate(Interval =  interval(ymd(start_dt),
                              ymd(end_dt)   )) %>%
  rowwise() %>%
  mutate(BBS_time =int_overlaps(Survey_dates, Interval))%>%
  filter(BBS_time | season == 'resident')

```

```{r eval = FALSE}
## This takes a little while to run

All_June_Range_Maps_GROUPED <-  All_June_Range_Maps_time %>%
  group_by(species_code ) %>%
  summarise(st_union(geom))


All_June_Range_Maps_GROUPED  %>%
  rename(geom =  `st_union(geom)`) %>%
  mutate(geom=   st_transform(geom, crs =4269 )) -> All_June_Range_Maps_GROUPED_coords

# save(All_June_Range_Maps_GROUPED_coords, file = '../Data/All_June_Range_Maps_GROUPED_coords')


InRange_all <- st_intersects(L48Routes$geometry,
                         All_June_Range_Maps_GROUPED_coords$geom , sparse=FALSE) 

save(InRange_all, file = '../Data/MatrixForm_transect_x_ebird_2')  

# All_June_Range_Maps_GROUPED_coords$species_code 
```

 [1] "abetow"  "acafly"  "acowoo"  "aldfly"  "allhum"  "altori"  "amecro"  "amegfi"  "amepip"  "amered"  "amerob"  "amtspa"
 [13] "annhum"  "arcwar1" "ariwoo"  "astfly"  "attwoo1" "audori"  "babwar"  "bacspa"  "baispa"  "balori"  "banswa"  "barswa"
 [25] "batpig1" "bawwar"  "belspa2" "belvir"  "benthr"  "bewwre"  "bicthr"  "bkbcuc"  "bkbmag1" "bkbwar"  "bkbwoo"  "bkcchi"
 [37] "bkchum"  "bkcspa"  "bkhgro"  "bkhpar"  "bkpwar"  "bkrfin"  "bktgna"  "bktspa"  "bkwvir"  "blctit4" "blkpho"  "blkswi"
 [49] "blueth"  "blugrb1" "blujay"  "bncfly"  "bnhcow"  "bnhnut"  "boboli"  "bohwax"  "borchi2" "botgra"  "brebla"  "brespa"
 [61] "britit"  "brncre"  "brnthr"  "brocow"  "brthum"  "btbwar"  "btnwar"  "btywar"  "bubhum"  "buggna"  "buhvir"  "bulori"
 [73] "bushti"  "buthum"  "buwwar"  "cacwre"  "calgna"  "calhum"  "calqua"  "calthr"  "caltow"  "camwar"  "cantow"  "canwar"
 [85] "canwre"  "carchi"  "carwre"  "casfin"  "caskin"  "casspa"  "casvir"  "cavswa"  "cedwax"  "cerwar"  "chbchi"  "chclon"
 [97] "chirav"  "chispa"  "chiswi"  "chswar"  "chukar"  "clanut"  "clcspa"  "cliswa"  "cogdov"  "comgra"  "commyn"  "comrav"
[109] "comred"  "comyel"  "corfly"  "coshum"  "coukin"  "cowscj1" "crithr"  "cubthr"  "daejun"  "dickci"  "dowwoo"  "ducfly"
[121] "dusfly"  "dusgro"  "easblu"  "easkin"  "easmea"  "easpho"  "eastow"  "eawpew"  "eaywag"  "eletro"  "eucdov"  "eursta"
[133] "eutspa"  "evegro"  "fiespa"  "fiscro"  "flsjay"  "foxspa"  "gamqua"  "gchwar"  "gcrfin"  "gilfli"  "gilwoo"  "gnttow"
[145] "gockin"  "gocspa"  "gofwoo"  "gowwar"  "graspa"  "grawar"  "grbani"  "grcfly"  "grekis"  "grepew"  "greroa"  "grnjay"
[157] "grpchi"  "grtgra"  "grycat"  "gryfly"  "gryjay"  "grykin"  "grypar"  "gryvir"  "gusgro"  "gycthr"  "haiwoo"  "hamfly"
[169] "harspa"  "henspa"  "heptan"  "herthr"  "herwar"  "hoared"  "hooori"  "hoowar"  "horlar"  "houfin"  "houspa"  "houwre"
[181] "hutvir"  "incdov"  "indbun"  "issjay"  "juntit1" "kenwar"  "kirwar"  "labwoo"  "laplon"  "larbun"  "larspa"  "lawgol"
[193] "lazbun"  "leafly"  "lecspa"  "lecthr"  "lepchi"  "lesgol"  "lewwoo"  "linspa"  "lobthr"  "logshr"  "louwat"  "luchum"
[205] "lucwar"  "macwar"  "maghum1" "magwar"  "mancuc"  "marwre"  "mcclon"  "mexchi"  "mexjay4" "monpar"  "monqua"  "moublu"
[217] "mouchi"  "moudov"  "mouqua"  "mouwar"  "naswar"  "nobtyr"  "norbob"  "norcar"  "norfli"  "normoc"  "norpar"  "norshr4"
[229] "norwat"  "norwhe"  "nrwswa"  "nstspa"  "nutman"  "nutwoo"  "oaktit"  "olispa"  "oliwar"  "olsfly"  "orcori"  "orcwar"
[241] "ovenbi1" "pacwre1" "paibun"  "paired"  "palwar"  "pasfly"  "phaino"  "phivir"  "pilwoo"  "pingro"  "pinjay"  "pinsis"
[253] "pinwar"  "placha"  "plsvir"  "prawar"  "prowar"  "purfin"  "purmar"  "pygnut"  "pyrrhu"  "rebnut"  "rebpig1" "rebsap"
[265] "rebwoo"  "recpar"  "recwoo"  "redcro"  "reevir1" "refwar"  "rehwoo"  "rensap"  "rewbla"  "rinphe"  "robgro"  "rocpig"
[277] "rocpta1" "rocwre"  "rotbec"  "rthhum"  "ruckin"  "rucspa"  "rufgro"  "rufhum"  "rugdov"  "rusbla"  "ruwspa"  "saggro"
[289] "sagspa1" "sagthr"  "savspa"  "saypho"  "scaqua"  "scatan"  "scoori"  "sctfly"  "seaspa"  "shicow"  "shtgro"  "smbani"
[301] "smilon"  "snobun"  "sonspa"  "soogro1" "spodov"  "spotow"  "sprgro"  "sprpip"  "sstspa"  "stejay"  "subfly"  "sumtan"
[313] "swaspa"  "swathr"  "swawar"  "tenwar"  "thbkin"  "towsol"  "towwar"  "treswa"  "tribla"  "trokin"  "tropar"  "tuftit"
[325] "varthr"  "vauswi"  "veery"   "verdin"  "verfly"  "vesspa"  "vichum"  "vigswa"  "virwar"  "warvir"  "wesblu"  "weskin"
[337] "wesmea"  "westan"  "wewpew"  "whbnut"  "whcpig2" "whcspa"  "whevir"  "whhwoo"  "whiwag"  "whtdov"  "whtpta1" "whtspa"
[349] "whtswi"  "whwcro"  "whwdov"  "wilfly"  "wilpta"  "wilsap"  "wiltur"  "winwre3" "wlswar"  "woewar1" "wooscj2" "woothr"
[361] "wrenti"  "yebcha"  "yebcuc"  "yebfly"  "yebmag"  "yebsap"  "yecpar"  "yeejun"  "yehbla"  "yelwar"  "yerwar"  "yetvir"
[373] "yetwar"

## Adding species with odd breeding dates

```{r eval = FALSE}
bird_codes_with_maps <- Ebird_Codes[Ebird_Codes %in% ebird_codes_withmaps]      

bird_codes_with_maps[!(bird_codes_with_maps %in% All_June_Range_Maps_GROUPED_coords$species_code)]
## "bkcvir1" "conwar"   ### don't appear

bird_codes_with_maps[!(bird_codes_with_maps %in% All_June_Range_Maps_GROUPED_coords$species_code)]%>%
  map_df(function(ebird_code){
    
    st_read(paste0('~/Downloads/all-range-2021.gpkg/',
                   ebird_code,'-range-mr-2021.gpkg'),
            layer = 'range',  quiet = TRUE) %>%
      return()
  }) -> All_June_Range_Maps_problems

All_June_Range_Maps_problems

#### some extras that were wrongly filtered out due to weird dates (now changed)
All_June_Range_Maps_problems %>%
  filter(season %in% c('resident','breeding'))%>%
  mutate(geom=   st_transform(geom, crs =4269 )) -> All_June_Range_Maps_GROUPED_coords_problems_toAdd
 
InRange_to_add <- st_intersects(L48Routes$geometry,
                         All_June_Range_Maps_GROUPED_coords_problems_toAdd$geom , sparse=FALSE) 
  
save(InRange_to_add, file = '../Data/MatrixForm_transect_x_ebird_EXTRAS')
```

## Finding total species pools


```{r}
load('../Data/All_June_Range_Maps_GROUPED_coords' )
load( '../Data/MatrixForm_transect_x_ebird_2')
load( '../Data/MatrixForm_transect_x_ebird_EXTRAS')

InRange_all_df <- as.data.frame(InRange_all)
colnames(InRange_all_df) <- All_June_Range_Maps_GROUPED_coords$species_code

InRange_all_df_toadd <- as.data.frame(InRange_to_add)
colnames(InRange_all_df_toadd) <- c("bkcvir1", "conwar")

InRange_all_df <- bind_cols(InRange_all_df, InRange_all_df_toadd)
InRange_all_df <- InRange_all_df%>%select(order(colnames(InRange_all_df)))  ## keep the alphabetical order of columns


InRange_all_df$RouteNumber <- L48Routes$RTENO

#### NB routes that turn back on themselves are in as separate rows of L48Routes, so need to be combined:

InRange_all_df %>%
  group_by(RouteNumber) %>%
  summarise(across(.fns =  any)) %>%
  left_join(AllRoutes, c('RouteNumber' = 'RTENO')) -> InRange_all_df_collapsed
 
# write_csv(InRange_all_df_collapsed, '../Data/InRange_all_df_collapsed.csv')
```

## Example Transect/Range Intersections

```{r fig.height=12}

InRange_all_df_collapsed %>%
  gather( Species, Present,   abetow:yetwar    ) %>%
  filter( str_starts(Species, 'a')) %>%
  ggplot(aes(x = Longitude, y = Latitude, col = Present))+
  geom_point(size =1)+
  facet_wrap(~Species, ncol = 3 )+
  ggtitle('Some Examples of species ranges intersected with transects')
```



# Session Info

```{r}
sessionInfo()
```






