---
title: "Inferring Curve Parameters from Hierarchical Model"
output: html_document
editor_options: 
  chunk_output_type: console
---

Because it is quite long and repetitive, pulling the machinery to calculate the inferred values from the hierarchical models here. 

Note also that this uses the model without the regression terms. 

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(vegan)  
library(purrr)
library(stringr)
library(posterior)

map <- purrr::map
select <- dplyr::select

logit <- function(x){return(log(x/(1-x)))}
inv_logit <- function(x){exp(x)/(1+exp(x))}
```

### Extracting model fitting summaries 

```{r message = FALSE}
STATS_select_scaled <- read_csv('../Data/STATS_select_SCALED.csv')

read_csv('../Data/All_Average_Curves.csv')%>%
  left_join(STATS_select_scaled, by = "TransectID") %>%
  filter( !is.na(Gamma_Div_Ebird))-> UnCenteredData
```

```{r}
EXTRACT_ALL_FUNC <- function(Model, BCR){
  print(BCR)
  draws <- as_draws_array(Model)
  Draw_summary <- summarise_draws(draws,  default_summary_measures(), default_convergence_measures())
  Draw_summary %>%mutate(BCR = BCR ) %>% return()
}

LOAD_MODELS_FUNC <- function(File){ x<- load(File);  return(Model)}
```

```{r eval = FALSE}
list_fits <- list.files('../ModelFits/NoPreds1/', full.names = TRUE)
Model_list <-map(list_fits, LOAD_MODELS_FUNC)
SummaryTable<- map2_df(Model_list,
                       str_extract(list_fits,  '[0-9]+$'),
                       EXTRACT_ALL_FUNC)

write_csv(SummaryTable, '../ModelSummaries/SummaryTable_NP1.csv')
```

```{r}
SummaryTable_WOPreds <- read_csv('../ModelSummaries/SummaryTable_NP1.csv')
```


# Centering data

```{r}
UnCenteredData %>%
  group_by(BCR) %>%
  summarise(mean_HM = mean(Av_HMindex),
            mean_CV = mean(CV_gpp_scaled),
            mean_AL = mean(AvRich_100),
            mean_GM = mean(Gamma_scaled) ) -> BCR_Means

# Center the data
UnCenteredData %>%
  left_join(BCR_Means, by = 'BCR') %>%
  mutate(C_HM = Av_HMindex-mean_HM,
         C_CV = CV_gpp-mean_CV,
         C_AL = AvRich_100-mean_AL,
         C_GM = Gamma_scaled-mean_GM) -> Data_filt_CENTERED

Data_filt_CENTERED %>%
  nest(data =c(x,y,n)) %>%
  select(TransectID, starts_with('C_')) %>%
  distinct()-> Centered_TransectStats
```

# Inferring curve values 

## d
```{r}
BCR_level_terms <- SummaryTable_WOPreds %>%
  filter(variable == 'b_logitd0_Intercept')%>%
  separate(variable, into =c('b', 'term', 'type'))%>% 
  select( term, Est. = median, BCR) %>%
  pivot_wider( id_cols = BCR, names_from = term, values_from = 'Est.')

Transect_level_terms <- SummaryTable_WOPreds %>%
  select( variable, RE_term =median      , BCR) %>% 
  filter(str_detect(variable ,pattern =  'r_TransectID__logitd0')) %>%
  mutate(TransectID  = str_sub(variable, 23,38 )) %>%
  select(-variable)

Transect_level_terms %>%
  left_join(BCR_level_terms, by = "BCR") %>%
  mutate( InferredD = inv_logit(logitd0 +RE_term   )) -> InferredD_FullModel
```

## L

```{r}

BCR_level_terms_L <- SummaryTable_WOPreds %>%
  filter(variable =='b_logL0_Intercept' )%>%
  separate(variable, into =c('b', 'term', 'type'))%>% 
  select( term, Est. = median      , BCR) %>%
  pivot_wider( id_cols = BCR, names_from = term, values_from = 'Est.')

Transect_level_terms_L <- SummaryTable_WOPreds %>%
  select( variable, RE_termL =median      , BCR) %>% 
  filter(str_detect(variable ,pattern =  'r_TransectID__logL0')) %>%
  mutate(TransectID  = str_sub(variable, 21,36 )) %>%
  select(-variable)

Transect_level_terms_L %>%
  left_join(BCR_level_terms_L, by = "BCR") %>%
  mutate( InferredL = exp(logL0  +RE_termL   )) -> InferredL_FullModel

```

## $\omega$

```{r}
BCR_level_terms_O <- SummaryTable_WOPreds %>%
  filter(variable == 'b_om0_Intercept')%>%
  separate(variable, into =c('b', 'term', 'type'))%>% 
  select( term, Est. = median      , BCR) %>%
  pivot_wider( id_cols = BCR, names_from = term, values_from = 'Est.')

SummaryTable_WOPreds %>%
    filter( str_detect(variable ,pattern =  'r_TransectID__om0' ))%>%
    select(variable, RE_termO = median      , BCR) %>%
    mutate(TransectID  = str_sub(variable, 19,34 )) -> Transect_level_terms_O

Transect_level_terms_O %>%
  left_join(BCR_level_terms_O, by = "BCR") %>%
  mutate( InferredO = om0 +RE_termO ) -> InferredO_FullModel

```

## Sigmas

```{r}
BCR_level_terms_Sig <- SummaryTable_WOPreds %>%
  filter(variable =='b_sigma_Intercept')%>% 
  select(InterceptSig = median, BCR) 

SummaryTable_WOPreds %>%
    filter( str_detect(variable ,pattern =  'r_TransectID__sigma' ))%>%
    select(variable, RE_termSig = median, BCR) %>%
    mutate(TransectID  = str_sub(variable, 19,34 )) -> Transect_level_terms_Sig

Transect_level_terms_Sig %>%
  left_join(BCR_level_terms_Sig, by = "BCR") %>%
  mutate( InferredSig_raw = InterceptSig+RE_termSig,
          InferredSig  = exp(InferredSig_raw)) -> InferredSig_FullModel

```

## Joining Together

```{r}
left_join(select(InferredD_FullModel,BCR , TransectID, InferredD),
          select(InferredO_FullModel, BCR , TransectID, InferredO),
          by = c("BCR", "TransectID")) %>%
left_join(select(InferredL_FullModel, BCR , TransectID, InferredL),
          by = c("BCR", "TransectID")) -> AllInferredCurveParams_woP

write_csv(AllInferredCurveParams_woP,'../ModelSummaries/AllCurveParams_WOPreds1.csv')

```

## Identifying Uncertainty in Estimates

Convert SD to VAR, then add, then return to SD

```{r}
BCR_level_terms_UNCERTAINTY <- SummaryTable_WOPreds %>%
  filter(variable %in% c('b_logitd0_Intercept', 'b_logL0_Intercept'))%>%
  separate(variable, into =c('b', 'term', 'type'))%>% 
  select( term, sd = sd, BCR) %>%
  pivot_wider( id_cols = BCR, names_from = term, values_from = 'sd')

Transect_level_terms_UNCERTAINTY_D0 <- SummaryTable_WOPreds %>%
  select( variable, RE_term_logitd0_sd =sd      , BCR) %>% 
  filter(str_detect(variable ,pattern =  'r_TransectID__logitd0')) %>%
  mutate(TransectID  = str_sub(variable, 23,38 )) %>%
  select(-variable)

Transect_level_terms_UNCERTAINTY_LO <- SummaryTable_WOPreds %>%
  select( variable, RE_term_logL0_sd =sd      , BCR) %>% 
  filter(str_detect(variable ,pattern =  'r_TransectID__logL0')) %>%
  mutate(TransectID  = str_sub(variable, 21,36 )) %>%
  select(-variable)

Transect_level_terms_UNCERTAINTY_D0 %>%
  left_join(Transect_level_terms_UNCERTAINTY_LO,
            by = c('BCR', "TransectID")) %>%
  left_join(BCR_level_terms_UNCERTAINTY,
            by = "BCR") %>%
  mutate( InferredD_SD =  sqrt(RE_term_logitd0_sd^2 + logitd0^2),
          InferredL_SD =  sqrt(RE_term_logL0_sd^2 + logL0^2)) -> Inferred_UnCertainty

write_csv(Inferred_UnCertainty,'../ModelSummaries/Inferred_UnCertaintyDL.csv')
```



# Session Info

```{r}
sessionInfo()
```



