---
title: "Prepping Parallel fit"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script combines the various pieces of predictor data and makes Figure 3 (the maps of the predictors and BCRs)

```{r}
library(tidyverse)
library(purrr)
library(stringr)
library(maps)
library(cowplot)
map <- purrr::map
select <- dplyr::select
```

## Transect Stats Data Input

```{R}
load(file = '../Data/2020Release_Nor/matrix_form_filt1')  ### list of matrices

TransectStats <- read_csv('../Data/TransectStats.csv')
AllRoutes<- read_csv('../Data/2020Release_Nor/routes.csv')%>%
  mutate(RTENO = parse_number(paste0(StateNum ,Route)))
RTENO_lookup <- read_csv('../Data/RTENO_lookup.csv')
Productivity <- read_csv('../Data/ProductivityTransects.csv')

InRange_all_df_collapsed <-read_csv('../Data/InRange_all_df_collapsed.csv')
InRange_all_df_collapsed %>%
  gather( Species, Present,   abetow:yetwar    ) %>%
  group_by(RouteNumber) %>%
  summarise( Gamma_Div_Ebird = sum(Present)) %>%
  mutate(RTENO = RouteNumber) -> Gamma_Div_Ebird_df

TransectStats %>%
  left_join(RTENO_lookup, by = "TransectID") %>%
  left_join(AllRoutes, by = "RTENO") %>%
  left_join(Productivity, by = "RTENO")%>%
  left_join(Gamma_Div_Ebird_df, by = "RTENO")-> STATS

```

```{R eval = FALSE}
write_csv(STATS, '../Data/STATS.csv')

STATS %>%
  select(  TransectID,RTENAME ,Average_Richness, BCR, CV_gpp,
           MEAN_gpp, Gamma_Div_Ebird ,Av_HMindex,Year_span   ) -> STATS_select

write_csv(STATS_select, '../Data/STATS_select.csv')
```

### Scaling statistics

So each of the predictors is approximately in the 0-1 range.
Using fixed transformations, so won't be impacted by any future changes in data filterring.
Human modification index already on 0-1, so using raw

```{r eval = FALSE}
STATS_select$Av_HMindex %>% hist
STATS_select %>%
mutate(AvRich_100 = Average_Richness/100,
       CV_gpp_scaled = sqrt(CV_gpp), 
       MEAN_gpp_scaled = MEAN_gpp/300,
       Gamma_scaled = Gamma_Div_Ebird/150) %>%
write_csv('../Data/STATS_select_SCALED.csv')
```

# Plots of transect Values (Figure 3)

```{r}
STATS <- read_csv('../Data/STATS.csv')
BCR_lookup <- read_csv('../Data/BCR_Lookup.csv')

  world_map <- map_data('world')
  USMAP<- map_data('state')

library(Polychrome)
BCRcolours <- unname(glasbey.colors(27))

Core_data <- STATS %>%
  filter(!is.na(Av_HMindex)) %>%
  arrange(BCR )%>%
  left_join(BCR_lookup,
            by = "BCR") %>%
  mutate( BCR_Name = paste0(BCR,': ', Name)) %>%
  add_count(BCR, name = 'NumInBCR') %>%
  filter(NumInBCR >= 25)
         
        
```


```{r}
         
CoreMAP <- Core_data %>%
  ggplot()+
  geom_map(aes(map_id=region ),data =  USMAP,
           map = USMAP, fill = 'grey70')+
  coord_quickmap(xlim = c(-125, -65), ylim = c(25, 50))+
  theme_nothing()+
  theme(legend.position  = c(0.2, 0),
        legend.direction = 'horizontal',
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 8))

## Humans
A <- CoreMAP+
  geom_point( aes(y=Latitude, x = Longitude, col = Av_HMindex))+
  scale_color_viridis_c(limits = c(0,0.8))+
    guides(col = guide_colorbar(title='Human Impact (HM)',
                            title.position = 'top' ))

## Variability

B <- CoreMAP+
  geom_point( aes(y=Latitude, x = Longitude, col = sqrt(CV_gpp) ))+
    scale_color_viridis_c(limits = c(0.1,0.6))+
    guides(col = guide_colorbar(title='Variability (CV)',
                            title.position = 'top' ))


## Gamma
C <- CoreMAP+  geom_point( aes(y=Latitude, x = Longitude, col = Gamma_Div_Ebird  ))+
      scale_color_viridis_c(limits = c(50,175))+
    guides(col = guide_colorbar(title= 'Species Pool (GM)',
                            title.position = 'top' ))

## Alpha 
D<- CoreMAP+  geom_point( aes(y=Latitude, x = Longitude, col = Average_Richness   ))+
        scale_color_viridis_c(limits = c(0,80))+
    guides(col = guide_colorbar(title='Species Richness (AL)',
                            title.position = 'top' ))

## Assembling
top<- plot_grid(A,B, C,D, nrow =1, labels = 'auto', label_fontface = 'plain')
```

```{r}
## BCR map

### Ordering BCRs

Core_data %>%
  distinct(BCR_Name) %>% 
  pluck('BCR_Name') -> BCR_names_ordered

E <- CoreMAP+
  geom_point( aes(y=Latitude, x = Longitude, colour = BCR_Name  ),
              shape = 19)+
  scale_colour_manual(values = BCRcolours,
                      guide_legend( title = 'Bird Conservation Region'), 
                      limits = BCR_names_ordered)+
  theme(legend.text = element_text(size =8),
        legend.key = element_rect(fill = 'grey70'))+
  guides(col = guide_legend(ncol = 3,
                            override.aes = c(size = 4) ,
                            title.position = 'top' ))

bot <- plot_grid(E+guides(col='none'),get_legend(E), rel_widths = c(2,3))


```

```{r}
## All together, predictor data
Fig3<- plot_grid(top, bot, ncol =1, rel_heights = c(1.5,2) ,
                 labels = c('', 'e'),  label_fontface = 'plain')
#Fig3 
ggsave('../MS_figs/Fig3_maps.png',Fig3,  width = 12, height = 6, bg = 'white')

```




