---
title: "Richness Trend Analyses"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document calculates the species richness trends for each transect, then examines for trends within and across the BCRs. 

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(brms)
library(posterior)
map <- purrr::map
select <- dplyr::select
```

## Transect Stats Data Input

```{R}
load(file = '../Data/2020Release_Nor/matrix_form_filt1')  ### list of matrices
STATS_scaled <- read_csv('../Data/STATS_select_SCALED.csv')
```

# Calculating Richness Through Time For Each Transect

```{r eval = FALSE}
matrix_form%>%
  map(   function(matrix_input){
    
    ### doing the filtering of very erratic years in here 
    
    if(nrow(matrix_input) ==1){return(data.frame(Trend = NA, R2 =NA))}
    
    Richnesses <- rowSums(matrix_input[,-1])
    LowerBound =  mean(Richnesses) -2 *sd(Richnesses)
    UpperBound =  mean(Richnesses) +2 *sd(Richnesses)
    YearsToKeep <- Richnesses>LowerBound & Richnesses<UpperBound
    matrix_input2<- matrix_input[YearsToKeep, ]
    df<-   data.frame(Year = matrix_input2[,1],
                      Richness = rowSums(matrix_input2[,-1]))

            if(nrow(df) <2){return(data.frame(Trend = NA, R2 =NA))}

    LM <- lm(data=df, Richness~Year)  
    
    Trend <- LM$coefficients[2]
    R2 <- summary(LM)$r.squared
    SE_trend =   sqrt(diag(vcov(LM)))[2] # calculate standard error of estimate
    
    return(data.frame(Trend = Trend,SE_trend=SE_trend,
                      R2 =R2, N_Years = nrow(df)))
  }) %>%
  map_dfr(.f = ~.,.id = 'TransectID')-> RichnessSlope_df

write_csv(RichnessSlope_df, '../ModelSummaries/RichnessSlope_df.csv')
```

# Overal Distribution of Richness Slopes

```{r}
RichnessSlope_df <- read_csv('../ModelSummaries/RichnessSlope_df.csv')

RichnessSlope_df %>%
  left_join(STATS_scaled, by = "TransectID") %>%
  filter(!is.na(Av_HMindex))%>%
  mutate(Year_span50 = Year_span/50)-> RichnessSlope_df_STATS
```

```{r}
RichnessSlope_df_STATS %>%
  ggplot(aes( Trend))+
  geom_histogram(binwidth = 0.02, )+
  geom_vline(xintercept = 0)+
  geom_vline(xintercept = mean(RichnessSlope_df_STATS$Trend), col = 2)+
  xlab('Species richness trend (species per year)')

RichnessSlope_df_STATS%>%
  ggplot(aes(y=Trend, x= Average_Richness))+
  geom_point()

RichnessSlope_df_STATS$Average_Richness %>% mean

mean(RichnessSlope_df_STATS$Trend / RichnessSlope_df_STATS$Average_Richness)*100*50
```

### Calculating Weights

Weighting each trend line by inverse of variance ($1/\sigma^2$)
```{r}
RichnessSlope_df_STATS$TrendWeight = 1/((RichnessSlope_df_STATS$SE_trend)^2) # 
RichnessSlope_df_STATS$TrendWeight %>% log10     %>%
  hist(main = 'Distribution of Weights')
```

### Mean Overall Trend in Species Richness
```{r}
RichnessSlope_df_STATS %>%
  group_by(BCR) %>%
  add_count(name = 'BCR_n') %>%
  filter(BCR_n >=25) %>% 
  lm(data = ., Trend ~ 1,weights = TrendWeight ) %>%
  summary()
```


# Within-BCR Linear Models

## Fitting linear models 

```{r eval = FALSE}
BCRs <- unique(RichnessSlope_df_STATS$BCR)

AllBCRs_Seperate_Richness<-map_df(BCRs, function(BCR_i){
  RichnessSlope_df_STATS %>%
    filter(BCR==BCR_i) -> filtdata

    lm(data = filtdata,
       Trend ~ Year_span50 +AvRich_100  + Av_HMindex +CV_gpp_scaled  +Gamma_scaled,
       weights = TrendWeight ) -> LM_fit 
  
  Coefs<-      as.data.frame(t(as.matrix(coefficients(LM_fit)))) 
  SEs <-           as.data.frame(t(as.matrix(  sqrt(diag(vcov(LM_fit))))))
  colnames(Coefs)<- paste0('Coefs',colnames(SEs))
  colnames(SEs)<- paste0('SE_',colnames(SEs))
  
  Coefs$R2 = summary(LM_fit)$r.squared
  Coefs$adjR2 = summary(LM_fit)$adj.r.squared
 Coefs$n = length(LM_fit$residuals)

  bind_cols(Coefs, SEs) %>%
    mutate(BCR = BCR_i) %>%
    return()
})

write_csv(AllBCRs_Seperate_Richness, '../ModelSummaries/Richness_AllBCRs_SeperateLM.csv' )
```



```{r}
AllBCRs_Seperate_Richness_uncut <- read_csv('../ModelSummaries/Richness_AllBCRs_SeperateLM.csv' )

### Take out BCRs that don't have at least 25 transects
AllBCRs_Seperate_Richness<- filter(AllBCRs_Seperate_Richness_uncut, n>=25)
```

# Overall 'Meta-analysis'

```{r eval = FALSE}
Richness_Overall_YS <- brm(bf(CoefsYear_span50    |se(SE_Year_span50)    ~1),
                              data = AllBCRs_Seperate_Richness,  silent = 2, refresh =0 )
Richness_Overall_HM    <- brm(bf(CoefsAv_HMindex   |se(SE_Av_HMindex )  ~1),
                              data = AllBCRs_Seperate_Richness, silent = 2, refresh =0 )
Richness_Overall_CV    <- brm(bf(CoefsCV_gpp_scaled|se(SE_CV_gpp_scaled)~1),
                              data = AllBCRs_Seperate_Richness )
Richness_Overall_AL    <- brm(bf( CoefsAvRich_100  |se(SE_AvRich_100 )  ~1),
                              data = AllBCRs_Seperate_Richness , silent = 2, refresh =0)
Richness_Overall_GM    <- brm(bf(CoefsGamma_scaled |se(SE_Gamma_scaled) ~1),
                              data = AllBCRs_Seperate_Richness , silent = 2, refresh =0)

bind_rows(summarise_draws(Richness_Overall_YS) %>% mutate( Predictor = 'YearSpan'),
          summarise_draws(Richness_Overall_HM)    %>% mutate( Predictor = 'Humans'),
          summarise_draws(Richness_Overall_CV)    %>% mutate( Predictor = 'CV'),
          summarise_draws(Richness_Overall_AL)    %>% mutate( Predictor = 'Alpha'),
          summarise_draws(Richness_Overall_GM)    %>% mutate( Predictor = 'Gamma')) -> Richness_Overall_Results

write_csv(Richness_Overall_Results, '../ModelSummaries/Richness_Overall_Results.csv')
```

## Quick Plot 

```{r}
Richness_Overall_Results <- read_csv('../ModelSummaries/Richness_Overall_Results.csv')

Richness_Overall_Results%>%
  filter(variable         =='b_Intercept')%>%
  ggplot( aes( x = Predictor))+
  geom_pointrange(aes(y = mean, ymin = q5, ymax = q95))+
  scale_colour_viridis_c()+
    geom_hline(yintercept =0)+
  ggtitle('Overall (Cross-BCR) Slope of Richness predictors')+
  coord_flip()
          
```


# Session Info

```{r}
sessionInfo()
```
