---
title: "Example Plots"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

This document makes the example plots for the paper: Main text figure 2, and SI figures. 


```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(vegan)  
library(purrr)
library(stringr)
library(cowplot)

map <- purrr::map
select <- dplyr::select

logit <- function(x){return(log(x/(1-x)))}
inv_logit <- function(x){exp(x)/(1+exp(x))}
```

### Reading in data

NB inferred curve parameters from the fitting process are calculated in `Inferring Curve Parameters from Hierarchical Model.rmd`

```{r message = FALSE, warning = FALSE}
SpNames <- read_csv('../Data/Consol_SpeciesNames.csv')
RawSims <- read_csv('../Data/2020Release_Nor/Dissim_Diff_df_filt2.csv') 
load(file = '../Data/2020Release_Nor/matrix_form_filt1')  ### list of matrices

STATS <- read_csv('../Data/STATS.csv')
STATS_select <- read_csv('../Data/STATS_select.csv')
STATS_select_scaled <- read_csv('../Data/STATS_select_SCALED.csv')

RichnessSlope_df <- read_csv('../ModelSummaries/RichnessSlope_df.csv')

STR_fit_df <- read_csv('../ModelSummaries/STR_AllBCRs_SeperateLM.csv')

## Reading in inferred slopes # Calculated in other .rmd. 
AllInferredCurveParams_woP <- read_csv('../ModelSummaries/AllCurveParams_WOPreds1.csv') %>%
  left_join(STATS_select)
```


# Focal Transect - Main Text Figure 2

```{r}
ExampleID <- 'C_840_S_02_R_008'  # has a nice flat richness trend, but fairly high d

RawPA_focal <- matrix_form[[which(names(matrix_form)==ExampleID)]]

## Species Names
SpNames %>%
  group_by(ConsolAOU) %>%
  summarise(Names = paste(English_Common_Name,
                          collapse = ' AND ')) -> CONSOL_Names

RawPA_focal %>%
  as.data.frame() %>%
  pivot_longer( names_to = 'Species', 
                values_to = 'Observed', -Year )%>%
  mutate(ConsolAOU = as.numeric(Species) ) %>%
  left_join(CONSOL_Names, by = "ConsolAOU") -> RawPA_focal_Long

FocalParams<-  filter(AllInferredCurveParams_woP, TransectID ==ExampleID)

```

## Panel B Richness Trends

```{r}
Richnesses <- rowSums(RawPA_focal[,-1])
LowerBound =  mean(Richnesses) -2 *sd(Richnesses)
UpperBound =  mean(Richnesses) +2 *sd(Richnesses)

YearsToKeep <- data.frame(Year =RawPA_focal[,1],
                          Richness = Richnesses,
                          Keep = Richnesses>LowerBound & Richnesses<UpperBound)

RawPA_focal_Long %>%
  filter(Observed ==1) %>%
  group_by(Year)%>%
  count() %>%
  left_join(YearsToKeep)-> RichnessData_focal

RichnessData_focal%>%
  filter(Keep) %>%
  ggplot(aes( x = Year, y = n))+
  geom_point()+
  geom_smooth(method = 'lm', se = FALSE,
              linetype = 'dashed', col = 'red')+
  geom_point( data = filter(RichnessData_focal, !Keep),
              col = 'grey' ) +
  theme_minimal()+
  scale_x_continuous(limits =  c(1965,2020), breaks = seq(1965,2020, by=5))+
  ylab('Number of Observed Species')+ xlab('Year')  -> Rich_plot

```

## Panel A Raw data

```{r}
## Reorder to have permanent species t the bottom
RawPA_focal_Long %>%
  group_by(Names,ConsolAOU) %>%
  filter( Observed==1) %>%
  summarise(FirstYear = min(Year),
            Occurences = n()) %>%
  arrange( FirstYear, desc(Occurences))-> SpeciesOrdering


RawPA_focal_Long %>%
  left_join(YearsToKeep, by = "Year") %>%
  ggplot(aes( x = Year, y = factor(ConsolAOU) ,
              fill = factor(Observed), 
              alpha = 0.5+(Keep/2)))+
  geom_tile()+
  scale_y_discrete(limits = factor(SpeciesOrdering$ConsolAOU)  )+
  scale_x_continuous(limits =  c(1965,2020), breaks = seq(1965,2020, by=5))+
  scale_fill_manual(values = c('yellow','black'))+
  theme_minimal()+
  theme(axis.text.y = element_blank())+
  ylab('Bird Species')+
  scale_alpha_identity()+guides(fill = 'none')  -> PA_plot
# 
# # With species names (very long, as some grouped)
# RawPA_focal_Long %>%
#   ggplot(aes( x = Year, y = Names, col = factor(Observed)))+
#   geom_point()+
#   scale_y_discrete(limits = SpeciesOrdering$Names )+
#     scale_x_continuous(limits =  c(1965,2025))

```

## Panel D Similartity Decay curve

```{r}

RawSims %>%
  filter( TransectID ==ExampleID) %>%
  mutate(Soren_sim = 1-SorenDist)-> Focal_rawDiffs

Focal_rawDiffs %>%
  select( TransectID, YearDiff, Soren_sim ) %>%
  group_by(TransectID, YearDiff) %>%
  summarise( y = mean(Soren_sim),
             SD=sd(Soren_sim),
             se_raw = sd(Soren_sim)/sqrt(n())) %>%
  mutate(  mean_sd = mean(SD,na.rm=TRUE),
           se = if_else(is.na(se_raw),mean_sd,se_raw )) %>%
  arrange(TransectID) %>%
  mutate(UsedForInitSlope = YearDiff<=8 )-> Focal_Averages

Focal_rawDiffs %>%
  left_join(FocalParams, by = "TransectID") %>%
  mutate(Curve =  InferredO*( (1-InferredD) * exp(-InferredL*YearDiff )+InferredD)) -> InferredCurveFocal

my_breaks = signif(exp(seq(from=log(0.005), to=log(0.035), l =4 )),2)

## Initial Slope



Focal_rawDiffs %>%
  ggplot(aes(x = YearDiff))+
  geom_point(aes( x = YearDiff, y = Soren_sim), size = 0.1, col = 'grey')+
  geom_smooth(data = filter(Focal_Averages,UsedForInitSlope),
              aes(x = YearDiff, y =y ),
              method = 'lm', se = FALSE)+
  geom_point(data = Focal_Averages,
             aes( x = YearDiff, y = y, col = se,
                  shape = UsedForInitSlope))+
  geom_line(data = InferredCurveFocal, aes(y =Curve), col = 'red', linetype = 2)+
  geom_hline(data = InferredCurveFocal,aes( yintercept =InferredD*InferredO), linetype=3)+
  geom_hline(data = InferredCurveFocal,aes( yintercept =InferredO), linetype= 3)+
  guides(shape = FALSE)+
  scale_color_viridis_c(trans = "log",option = 'plasma',
                        breaks = my_breaks, labels = my_breaks,
                        limits = c(0.005, 0.035), name = 'SE')+
  ylab('Sørensen Similarity')+ #theme(legend.position = 'bottom')+
  xlab('Years Between Samples')+
  theme_minimal()+
  theme(legend.position = c(0.6, 0.85),
        legend.direction = 'horizontal',
        legend.title = element_text(size = 10),
        legend.key.width = unit(0.6, "cm"),
        legend.key.height  = unit(0.5, "cm"),
        legend.text = element_text(size = 8))   -> Sim_Plot



```

## Panel C Species Accumulation Curve

```{R}
Focal_mat <- RawPA_focal[,-1]
N_years = nrow(Focal_mat)

XX <- specaccum(Focal_mat, method = 'collector')


str_data<- data.frame( sample = 1:nrow(Focal_mat),
                       Year =RawPA_focal[,1],
                       accum_richness= XX$richness) %>%
  mutate(Time = Year-min(Year),
         log_time = log(Time), 
         log_accum_richness = log(accum_richness))%>%
  mutate(Cut = sample  <5 ) 

str_fit <- lm(log_accum_richness~log_time, data = filter(str_data,!Cut ))  # drop first four points
LogSc <- coefficients(str_fit)[1]
LogSw <- coefficients(str_fit)[2]
LogSLogT_r2 <- summary(str_fit)$r.squared

str_data %>%
  filter( !Cut) %>%
  ggplot(aes( x = log_time , y = log_accum_richness))+
  geom_smooth(method = 'lm', se = FALSE,
              linetype = 'dashed', col = 'red')+
  geom_point()+
  ylab('Accumulated Species\nRichness (log)')+
  xlab('Years Since First Survey (log)')+
  theme_minimal()+
  geom_point( data = filter(str_data, Cut),
              col = 'grey' )->STR_plot

```

## Combining into Figure 2
```{r}

Fig2ExampleSet<-plot_grid( PA_plot, Rich_plot,STR_plot, Sim_Plot, labels = 'auto')
Fig2ExampleSet

ggsave('../MS_figs/Fig2_example.png', Fig2ExampleSet,
       width = 10, height = 8, bg = 'white' )

```


## New version of Figure 2
```{r}

Fig2ExampleSet<-plot_grid( PA_plot ,Sim_Plot,STR_plot, 
                           labels = c('a) Species presence-absence matrix',
                                      'b) Community similarity decay',
                                      'c) Rate of species accumulation') ,
                           scale = 0.85,
                           hjust = -0.1, 
                           ncol= 1)
Fig2ExampleSet

ggsave('../MS_figs/Fig2_v2.png', Fig2ExampleSet,
       width = 5, height = 9, bg = 'white' )

```






### Information about example plot

```{r}
paste('Transect = :', ExampleID)

STATS %>% filter(TransectID == ExampleID) %>% pluck('RouteName')
paste('Transect = :', FocalParams$TransectID)

STATS %>% filter(TransectID == ExampleID) %>%
  pluck('BCR') ## Appalachian Mountains  (lower end)

STATS %>% filter(TransectID == ExampleID) %>%
  pluck('StateNum') ## Alabama

STATS %>% filter(TransectID == ExampleID) %>%
  select(Latitude, Longitude) ## Appalachian Mountains


paste('exponent:', signif(LogSw,3))

paste('d:', signif(FocalParams$InferredD,3),
      'o:', signif(FocalParams$InferredO,3),
      'L:', signif(FocalParams$InferredL,3))

paste('trend:',
      signif(filter(RichnessSlope_df,
                    TransectID == ExampleID)$Trend,3))

```

# SI Figure - Set of example similarity decay curves

Random selection of  transects
```{r}
set.seed(13)
AllInferredCurveParams_woP %>%
  slice_sample( n=10 ) -> SampledCurves

RawSims %>%
  filter( TransectID%in% SampledCurves$TransectID) %>%
  mutate(Soren_sim = 1-SorenDist)-> SampledCurves_rawDiffs

SampledCurves_rawDiffs %>%
  select( TransectID, YearDiff, Soren_sim ) %>%
  group_by(TransectID, YearDiff) %>%
  summarise( y = mean(Soren_sim),
             SD=sd(Soren_sim),
             se_raw = sd(Soren_sim)/sqrt(n())) %>%
  mutate(  mean_sd = mean(SD,na.rm=TRUE),
           se = if_else(is.na(se_raw),mean_sd,se_raw )) %>%
  arrange(TransectID)  -> SampledCurves_Averages

SampledCurves_rawDiffs %>%
  left_join(select(AllInferredCurveParams_woP,                ## without predictor curves
                   TransectID       , BCR,
                   NP_InferredD=  InferredD ,
                   NP_InferredO=InferredO ,
                   NP_InferredL=  InferredL), by = "TransectID") %>%
  mutate(NP_Curve =  NP_InferredO*( (1-NP_InferredD) * exp(-NP_InferredL*YearDiff )+NP_InferredD)) -> InferredCurves

SampledCurves_rawDiffs %>%
  ggplot(aes(x = YearDiff))+
  geom_point(aes( x = YearDiff, y = Soren_sim), size = 0.1, col = 'grey')+
  geom_point(data = SampledCurves_Averages,  aes( x = YearDiff, y = y, col = se))+
  geom_line(data = InferredCurves, aes(y =NP_Curve , group = TransectID), col = 'red')+
  scale_color_viridis_c(name = 'SE of interval average')+
  facet_wrap(~TransectID, nrow=2)+
  theme_minimal()+
  scale_y_continuous(limits = c(0.35, 1))+
  geom_text(data = InferredCurves,
            aes(label = paste0('BCR:', BCR,
                               ' d: ', signif(NP_InferredD,2),
                               '\nL: ', signif(NP_InferredL,2),
                               ' ω: ', signif(NP_InferredO,2))),
            y= 0.4, x = 2, hjust = 0, size = 3 )+
  theme(legend.position = 'bottom', legend.text = element_text(angle = -90 , hjust = 0 ))+
  xlab('Year Difference')+
  ylab('Sorensen Similarity')-> TenExamples

TenExamples

```

## Examples that show strong levelling off

```{r}
## Examples that show strong levelling off 
ExamplesToUse <- c('C_840_S_81_R_024', 'C_840_S_14_R_409', 'C_840_S_92_R_041', 
                   'C_840_S_14_R_023', 'C_840_S_49_R_047', 'C_840_S_64_R_018', 
                   'C_840_S_81_R_009', 'C_840_S_85_R_310', 'C_840_S_92_R_071',
                   'C_840_S_92_R_093')

RawSims %>%
  filter( TransectID%in% ExamplesToUse) %>%
  mutate(Soren_sim = 1-SorenDist)-> SampledCurves_rawDiffs

SampledCurves_rawDiffs %>%
  select( TransectID, YearDiff, Soren_sim ) %>%
  group_by(TransectID, YearDiff) %>%
  summarise( y = mean(Soren_sim),
             SD=sd(Soren_sim),
             se_raw = sd(Soren_sim)/sqrt(n())) %>%
  mutate(  mean_sd = mean(SD,na.rm=TRUE),
           se = if_else(is.na(se_raw),mean_sd,se_raw )) %>%
  arrange(TransectID)  -> SampledCurves_Averages

SampledCurves_rawDiffs %>%
  left_join(select(AllInferredCurveParams_woP,## without predictor curves
                   TransectID       ,BCR,
                   NP_InferredD=  InferredD ,
                   NP_InferredO=InferredO ,
                   NP_InferredL=  InferredL), by = "TransectID") %>%
  mutate(NP_Curve =  NP_InferredO*( (1-NP_InferredD) * exp(-NP_InferredL*YearDiff )+NP_InferredD)) -> InferredCurves

SampledCurves_rawDiffs %>%
  ggplot(aes(x = YearDiff))+
  geom_point(aes( x = YearDiff, y = Soren_sim), size = 0.1, col = 'grey')+
  geom_point(data = SampledCurves_Averages,  aes( x = YearDiff, y = y, col = se))+
  geom_line(data = InferredCurves, aes(y =NP_Curve , group = TransectID), col = 'red')+
  scale_color_viridis_c()+
  scale_y_continuous(limits = c(0.35, 1))+
  facet_wrap(~TransectID, nrow=2)+
  theme_minimal()+
  geom_text(data = InferredCurves,
            aes(label = paste0('BCR:', BCR,
                               ' d: ', signif(NP_InferredD,2),
                               '\nL: ', signif(NP_InferredL,2),
                               ' ω: ', signif(NP_InferredO,2))),
            y= 0.4, x = 2, hjust = 0, size = 3 )+
  theme(legend.position = 'bottom', legend.text = element_text(angle = -90 , hjust = 0 ))+
  xlab('Year Difference')+
  ylab('Sorensen Similarity')-> Ten_Clear_Examples

Ten_Clear_Examples

```

## Combining

```{r}

plot_grid( TenExamples+guides(col='none'),
           Ten_Clear_Examples+guides(col='none'),
           get_legend(TenExamples),
           
           labels = c('a) Ten random examples',
                      'b) Ten examples that show particuarly clear levelling off',
                      ''),
           scale = 0.9, hjust = -0.1,
           nrow=3, rel_heights = c(5,5,1)) -> Examples_bothtypes

ggsave('../MS_figs/SI4_10_10ClearExamples.png',
       Examples_bothtypes,
       width = 8, height = 12, bg = 'white' )

ggsave('../MS_figs/SI4_10_10ClearExamples.pdf',
       Examples_bothtypes,
       width = 8, height = 12, bg = 'white' )

```


# Session Info

```{r}
sessionInfo()
```


