---
title: "Similarity Decay Analysis (B_SIM alternative analysis)"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

This document reads in the BCR-level similarity decay curve fitting results, and carries out the 'meta-analysis' (cross-BCR) analysis. 

It is a simplified repeat of the main `Similarity Decay Analysis` script that uses the alternative $\beta_{sim}$ measure of turnover. 

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(vegan)  
library(purrr)
library(brms)
library(stringr)
library(bayesplot)
library(tidybayes)
library(posterior)
library(cowplot)
library(scales)
library(betapart)
library(broom)

map <- purrr::map
select <- dplyr::select

logit <- function(x){return(log(x/(1-x)))}
inv_logit <- function(x){exp(x)/(1+exp(x))}

STATS <- read_csv('../Data/STATS.csv')
STATS_select <- read_csv('../Data/STATS_select.csv')
STATS_select_scaled <- read_csv('../Data/STATS_select_SCALED.csv')

```

# Calculating Dissimilarities

Here calculating all three measures of similarity. 

```{r eval = FALSE}

# load(file = '../Data/2020Release_Nor/matrix_form_filt1')  ### list of matrices

matrix_form %>%
  map(   function(matrix_input){
    
    if(nrow(matrix_input)==1){ ## catch annoying short year that sneaks through
      return(data.frame(Year1 = matrix_input[1,1],Year2 =  matrix_input[1,1] , YearDiff = 0,  JaccDist = 0,  SorenDist = 0) )}
    
    ### doing the filtering of very erratic yearss in here (NB will need to carry over into other functions that use matrix_form)
    Richnesses <- rowSums(matrix_input[,-1])
    LowerBound =  mean(Richnesses) -2 *sd(Richnesses)
    UpperBound =  mean(Richnesses) +2 *sd(Richnesses)
    YearsToKeep <- Richnesses>LowerBound & Richnesses<UpperBound
    matrix_input<- matrix_input[YearsToKeep, ]
    
    YEARS <- matrix_input[,1]
    YearDiff<-as.matrix(dist(YEARS))
    JaccDist <- as.matrix(vegdist(matrix_input[,-1],method = 'jaccard' ))
    SorenDist <- as.matrix(vegdist(matrix_input[,-1],method = 'bray' ))
    
    PartitionedSorensen <-beta.pair(matrix_input[,-1])
    Soren_BaselTurn_Dist <- as.matrix(PartitionedSorensen$beta.sim)
    Soren_BaselNest_Dist <- as.matrix(PartitionedSorensen$beta.sne)
    Soren_BaselTOTA_Dist <- as.matrix(PartitionedSorensen$beta.sor)
    
    data.frame(Year1 = rep(YEARS,length(YEARS)) ,
               Year2 = rep(YEARS,each = length(YEARS)) ,
               YearDiff = as.vector(YearDiff),
               JaccDist = as.vector(JaccDist),
               SorenDist = as.vector(SorenDist),
               Soren_BaselTurnDist = as.vector(Soren_BaselTurn_Dist),
               Soren_BaselNestDist = as.vector(Soren_BaselNest_Dist),
               Soren_BaselTOTADist = as.vector(Soren_BaselTOTA_Dist)) %>%
      filter( Year1 < Year2) %>%
      return()
  }) %>%
  map_dfr(.f = ~.,.id = 'TransectID')-> Sim_Diff_df

write_csv(Sim_Diff_df, '../Data/2020Release_Nor/Dissim_Diff_df_filt3.csv')  
```

## Processing and Filtering out very short datasets
```{r eval = FALSE}
Sim_Diff_df<- read_csv('../Data/2020Release_Nor/Dissim_Diff_df_filt3.csv')

Sim_Diff_df %>%
  group_by(TransectID ) %>%
  mutate( Start = min(Year1), 
          N_Returns = n_distinct(Year2 )) %>%
  filter(N_Returns>10) -> Sim_AllPairs

All_IDS<- unique(Sim_AllPairs$TransectID)

Sim_AllPairs %>%
  mutate(Turn_sim = 1-Soren_BaselTurnDist) %>%     ### Switching this to just Turnover component of Sorensen
  select( TransectID, YearDiff, Turn_sim ) %>%     ### Switching this to just Turnover component of Sorensen
  group_by(TransectID, YearDiff) %>%
  summarise( y = mean(Turn_sim),         ### Switching this to just Turnover component of Sorensen
             n = n(),
             SD=sd(Turn_sim),    ### Switching this to just Turnover component of Sorensen
             se_raw = sd(Turn_sim)/sqrt(n())) %>%
  mutate(  mean_sd = mean(SD,na.rm=TRUE),
           se = if_else(is.na(se_raw),mean_sd,se_raw )) %>%
  rename(x = YearDiff) %>%
  arrange(TransectID)  -> Average_Curves

```

## Removing positive similarity time distance 

Filter out any that show a positive linear relationship between similarity and time (indicates something very odd going on)

```{r eval =FALSE}
Average_Curves %>%
  nest(data = -TransectID) %>%
  mutate(fit = map(data, ~ lm(y~x  , data = .x)),
         tidied = map(fit, tidy)  ) %>%
  unnest(tidied) %>%
  filter( term == 'x') -> LinearFits

LinearFits %>%
  arrange( desc(estimate)) %>%
  filter( !(p.value>0.05  | estimate <0) )   # 150 transects to remove?

## Comapring to richness trends 
RichnessSlope_df %>%
  left_join(LinearFits) %>%
  ggplot(aes( x = Trend,y = estimate, col = p.value<0.05))+
  geom_hline(yintercept = 0)+
  geom_point(alpha=0.2)+
  xlab('Richness Trend')+
  ylab(' Similarity - Time linear slope' ) +
  scale_x_continuous(limits = c( -3,3))+
  ggtitle('Strong Richness trends are associated with positive slopes',
          'this is Basega Turnover, which is meant ot take out species number trends' )

RichnessSlope_df %>%
  left_join(LinearFits) %>%
  left_join(STATS_select_scaled) %>%
  mutate(ProblemSlope = !(p.value>0.05  | estimate <0) ) %>%
  filter( !is.na(estimate )) %>%
  lm(data=., ProblemSlope~  AvRich_100 +CV_gpp_scaled +MEAN_gpp_scaled+Year_span_scaled+Gamma_scaled  ) %>%
  summary()

Average_Curves %>%
  left_join(LinearFits, by = 'TransectID') %>%
  filter( (p.value>0.05  | estimate <0) )  %>%
  select( -(data: p.value)) -> Average_Curves

write_csv(Average_Curves, '../Data/All_Average_Curves_3.csv')
```

# Record of HPC Scripts used

The main model fitting is conducted in parallel on HPC: 

### `Stanfit_All_2024.R`

```{r, file='../Scripts/Stanfit_All_2024.R', eval = FALSE}
```

# Processing raw results

(NB calculating posterior summary statistics takes a few minutes)

```{r}
EXTRACT_ALL_FUNC <- function(Model, BCR){
  print(BCR)
  draws <- as_draws_array(Model)
  Draw_summary <- summarise_draws(draws,  default_summary_measures(), default_convergence_measures())
  Draw_summary %>%mutate(BCR = BCR ) %>% return()
}

LOAD_MODELS_FUNC <- function(File){ x<- load(File);  return(Model)}
```

```{r eval = FALSE}
RE_Human <- list.files('../ModelFits/All_preds_2024/', full.names = TRUE)  ## changed
Model_list_RE_Human <-map(RE_Human, LOAD_MODELS_FUNC)
SummaryTableRE_Human<- map2_df(Model_list_RE_Human,
                               str_extract(RE_Human,  '[0-9]+$'),
                               EXTRACT_ALL_FUNC)
write_csv(SummaryTableRE_Human, '../ModelSummaries/SummaryTable_ALL_2024.csv')    ## changed
```

### Saving example STAN scripts 

Included here just for reference - all fitting is done by brms. 

```{r eval = FALSE}

Model_list_RE_Human[[1]]$model

Model_list_RE_Human[[1]]$prior

```

# Overall Results

```{r message = FALSE}
SummaryTableRE_Human <- read_csv('../ModelSummaries/SummaryTable_ALL_2024.csv')   ## changed
SummaryTableRE_Human
```

## Fitting 'Overall' Models

Separate models fit for each curve parameter and each predictor. 

```{r message = FALSE, results='hide',warning = FALSE, eval =FALSE}
SummaryTableRE_Human%>% 
  filter(str_detect(variable, 'beta'))%>%
  mutate(Response = str_sub(variable,7,7),
         Predictor = str_sub(variable,8,9)) %>%
  select( Response, Predictor,mean, sd, BCR) -> CurveFitEsts

## Compile model once

ModelBase_MAcurve    <- brm(bf(mean|se(sd)~1), data = CurveFitEsts, iter =5000 , silent = 2, refresh =0)

Curve_d_Overall_HM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'HM')))
Curve_d_Overall_CV    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'CV')))
Curve_d_Overall_AL    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'AL')))
Curve_d_Overall_GM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'GM')))
Curve_d_Overall_YS    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'YS')))

Curve_L_Overall_HM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'HM')))
Curve_L_Overall_CV    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'CV')))
Curve_L_Overall_AL    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'AL')))
Curve_L_Overall_GM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'GM')))
Curve_L_Overall_YS    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'YS')))

Curve_o_Overall_HM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'HM')))
Curve_o_Overall_CV    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'CV')))
Curve_o_Overall_AL    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'AL')))
Curve_o_Overall_GM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'GM')))
Curve_o_Overall_YS    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'YS')))

Curve_d_Overall_HM$Response <- 'd' 
Curve_d_Overall_CV$Response <- 'd' 
Curve_d_Overall_AL$Response <- 'd' 
Curve_d_Overall_GM$Response <- 'd' 
Curve_d_Overall_YS$Response <- 'd' 

Curve_L_Overall_HM$Response <- 'L' 
Curve_L_Overall_CV$Response <- 'L' 
Curve_L_Overall_AL$Response <- 'L' 
Curve_L_Overall_GM$Response <- 'L' 
Curve_L_Overall_YS$Response <- 'L' 

Curve_o_Overall_HM$Response <- 'o' 
Curve_o_Overall_CV$Response <- 'o' 
Curve_o_Overall_AL$Response <- 'o' 
Curve_o_Overall_GM$Response <- 'o' 
Curve_o_Overall_YS$Response <- 'o' 


Curve_d_Overall_HM$Predictor = 'HM'
Curve_d_Overall_CV$Predictor = 'CV'
Curve_d_Overall_AL$Predictor = 'AL'
Curve_d_Overall_GM$Predictor = 'GM'
Curve_d_Overall_YS$Predictor = 'YS'

Curve_L_Overall_HM$Predictor = 'HM'
Curve_L_Overall_CV$Predictor = 'CV'
Curve_L_Overall_AL$Predictor = 'AL'
Curve_L_Overall_GM$Predictor = 'GM'
Curve_L_Overall_YS$Predictor = 'YS'

Curve_o_Overall_HM$Predictor = 'HM'
Curve_o_Overall_CV$Predictor = 'CV'
Curve_o_Overall_AL$Predictor = 'AL'
Curve_o_Overall_GM$Predictor = 'GM'
Curve_o_Overall_YS$Predictor = 'YS'


bind_rows(Curve_d_Overall_HM,
          Curve_d_Overall_CV,
          Curve_d_Overall_AL,
          Curve_d_Overall_GM,
          Curve_d_Overall_YS,
          Curve_L_Overall_HM,
          Curve_L_Overall_CV,
          Curve_L_Overall_AL,
          Curve_L_Overall_GM,
          Curve_L_Overall_YS,
          Curve_o_Overall_HM,
          Curve_o_Overall_CV,
          Curve_o_Overall_AL,
          Curve_o_Overall_GM ,
          Curve_o_Overall_YS) %>%
  filter(variable=='b_Intercept') -> AllCurveCoefs

write_csv(AllCurveCoefs,'../ModelSummaries/AllCurveCoefs_2024.csv') ## changed
```

## Rough Plot
```{r}
AllCurveCoefs<- read_csv('../ModelSummaries/AllCurveCoefs_2024.csv')

AllCurveCoefs

AllCurveCoefs%>%
  ggplot( aes( x = Predictor))+
  geom_pointrange(aes(y = mean, ymin = q5, ymax = q95))+
  scale_colour_viridis_c()+
  geom_hline(yintercept =0)+
  facet_wrap(Response~., ncol=1)+
  ggtitle('Overall (Cross-BCR) Turnover Curve Predictors')+
  coord_flip()
```


# Session Info

```{r}
sessionInfo()
```
