---
title: "Similarity Decay Analysis"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

This document reads in the BCR-level similarity decay curve fitting results, and carries out the 'meta-analysis' (cross-BCR) analysis. 

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(vegan)  
library(purrr)
library(brms)
library(stringr)
library(bayesplot)
library(tidybayes)
library(posterior)
library(cowplot)
library(scales)

map <- purrr::map
select <- dplyr::select

logit <- function(x){return(log(x/(1-x)))}
inv_logit <- function(x){exp(x)/(1+exp(x))}


STATS <- read_csv('../Data/STATS.csv')
STATS_select <- read_csv('../Data/STATS_select.csv')
STATS_select_scaled <- read_csv('../Data/STATS_select_SCALED.csv')

AllInferredCurveParams<- read_csv('../ModelSummaries/AllCurveParams_WOPreds1.csv') # made elsewhere (Inferring Curve Parameters...)

```

# Calculating Dissimilarities

```{r eval = FALSE}
# load(file = '../Data/2020Release_Nor/matrix_form_filt1') 
# kept just for reference
matrix_form %>%
  map(   function(matrix_input){

    if(nrow(matrix_input)==1){ ## catch annoying short year that sneaks through
      return(data.frame(Year1 = matrix_input[1,1],Year2 =  matrix_input[1,1] , YearDiff = 0,  JaccDist = 0,  SorenDist = 0) )}

    ### doing the filtering of very erratic yearss in here (NB will need to carry over into other functions that use matrix_form)
    Richnesses <- rowSums(matrix_input[,-1])
      LowerBound =  mean(Richnesses) -2 *sd(Richnesses)
      UpperBound =  mean(Richnesses) +2 *sd(Richnesses)
      YearsToKeep <- Richnesses>LowerBound & Richnesses<UpperBound
      matrix_input<- matrix_input[YearsToKeep, ]

    YEARS <- matrix_input[,1]
    YearDiff<-as.matrix(dist(YEARS))
    JaccDist <- as.matrix(vegdist(matrix_input[,-1],method = 'jaccard' ))
    SorenDist <- as.matrix(vegdist(matrix_input[,-1],method = 'bray' ))
    data.frame(Year1 = rep(YEARS,length(YEARS)) ,
               Year2 = rep(YEARS,each = length(YEARS)) ,
               YearDiff = as.vector(YearDiff),
               JaccDist = as.vector(JaccDist),
               SorenDist = as.vector(SorenDist)) %>%
      filter( Year1 < Year2) %>%
      return()
  }) %>%
  map_dfr(.f = ~.,.id = 'TransectID')-> Sim_Diff_df

write_csv(Sim_Diff_df, '../Data/2020Release_Nor/Dissim_Diff_df_filt2.csv')  
```

## Processing and Filtering out very short datasets
```{r eval = FALSE}
Sim_Diff_df<- read_csv('../Data/2020Release_Nor/Dissim_Diff_df_filt2.csv')

Sim_Diff_df %>%
  group_by(TransectID ) %>%
  mutate( Start = min(Year1), 
          N_Returns = n_distinct(Year2 )) %>%
  filter(N_Returns>10) -> Sim_AllPairs

All_IDS<- unique(Sim_AllPairs$TransectID)

Sim_AllPairs %>%
  mutate(Soren_sim = 1-SorenDist) %>%
  select( TransectID, YearDiff, Soren_sim ) %>%
  group_by(TransectID, YearDiff) %>%
  summarise( y = mean(Soren_sim),
             n = n(),
             SD=sd(Soren_sim),
             se_raw = sd(Soren_sim)/sqrt(n())) %>%
  mutate(  mean_sd = mean(SD,na.rm=TRUE),
           se = if_else(is.na(se_raw),mean_sd,se_raw )) %>%
  rename(x = YearDiff) %>%
  arrange(TransectID)  -> Average_Curves

write_csv(Average_Curves, '../Data/All_Average_Curves.csv')
```

### Table of BCRs to fit
```{r eval = FALSE}
Average_Curves %>%
  nest() %>%
  left_join(STATS_select, by = "TransectID")%>%
  filter( !is.na(Gamma_Div_Ebird))%>%
  ungroup() %>%
  count(BCR) %>%
  arrange(BCR) %>%
  filter(n>=25) -> BCRsToFit

write_csv(BCRsToFit, '../Data/BCRsToFit.csv')
```

# Record of HPC Scripts used

The main model fitting is conducted in parallel on HPC. 

### `Stanfit_All3.R`

For the 'inbuilt' regression.

```{r, file='../Scripts/Stanfit_All3.R', eval = FALSE}
```

### `Stanfit_noPreds.R`

For the direct fitting, to extract the fitted parameters without additional errors. 

```{r, file='../Scripts/Stanfit_noPreds.R', eval = FALSE}
```

# Processing raw results

(NB calculating posterior summary statistics takes a few minutes)

```{r}
EXTRACT_ALL_FUNC <- function(Model, BCR){
  print(BCR)
  draws <- as_draws_array(Model)
  Draw_summary <- summarise_draws(draws,  default_summary_measures(), default_convergence_measures())
  Draw_summary %>%mutate(BCR = BCR ) %>% return()
}

LOAD_MODELS_FUNC <- function(File){ x<- load(File);  return(Model)}
```

```{r eval = FALSE}
RE_Human <- list.files('../ModelFits/All_preds3/', full.names = TRUE)
Model_list_RE_Human <-map(RE_Human, LOAD_MODELS_FUNC)
SummaryTableRE_Human<- map2_df(Model_list_RE_Human,
                               str_extract(RE_Human,  '[0-9]+$'),
                               EXTRACT_ALL_FUNC)
write_csv(SummaryTableRE_Human, '../ModelSummaries/SummaryTable_ALL3.csv')
```

### Saving example STAN scripts 

Included here just for reference - all fitting is done by brms. 

```{r eval = FALSE}

Model_list_RE_Human[[1]]$model


Model_list_RE_Human[[1]]$prior

```


# Overall Results

```{r message = FALSE}
SummaryTableRE_Human <- read_csv('../ModelSummaries/SummaryTable_ALL3.csv')
SummaryTableRE_Human
```

## Fitting 'Overall' Models

Sperate models fit for each curve parameter and each predictor. 

```{r message = FALSE, results='hide',warning = FALSE}
SummaryTableRE_Human%>% 
  filter(str_detect(variable, 'beta'))%>%
  mutate(Response = str_sub(variable,7,7),
         Predictor = str_sub(variable,8,9)) %>%
  select( Response, Predictor,mean, sd, BCR) -> CurveFitEsts

## Compile model once

ModelBase_MAcurve    <- brm(bf(mean|se(sd)~1), data = CurveFitEsts, iter =5000 , silent = 2, refresh =0)

Curve_d_Overall_HM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'HM')))
Curve_d_Overall_CV    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'CV')))
Curve_d_Overall_AL    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'AL')))
Curve_d_Overall_GM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'GM')))
Curve_d_Overall_YS    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'd', Predictor == 'YS')))

Curve_L_Overall_HM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'HM')))
Curve_L_Overall_CV    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'CV')))
Curve_L_Overall_AL    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'AL')))
Curve_L_Overall_GM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'GM')))
Curve_L_Overall_YS    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'L', Predictor == 'YS')))

Curve_o_Overall_HM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'HM')))
Curve_o_Overall_CV    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'CV')))
Curve_o_Overall_AL    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'AL')))
Curve_o_Overall_GM    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'GM')))
Curve_o_Overall_YS    <-summarise_draws(update(ModelBase_MAcurve,
                                               newdata =  filter(CurveFitEsts, Response == 'o', Predictor == 'YS')))

Curve_d_Overall_HM$Response <- 'd' 
Curve_d_Overall_CV$Response <- 'd' 
Curve_d_Overall_AL$Response <- 'd' 
Curve_d_Overall_GM$Response <- 'd' 
Curve_d_Overall_YS$Response <- 'd' 

Curve_L_Overall_HM$Response <- 'L' 
Curve_L_Overall_CV$Response <- 'L' 
Curve_L_Overall_AL$Response <- 'L' 
Curve_L_Overall_GM$Response <- 'L' 
Curve_L_Overall_YS$Response <- 'L' 

Curve_o_Overall_HM$Response <- 'o' 
Curve_o_Overall_CV$Response <- 'o' 
Curve_o_Overall_AL$Response <- 'o' 
Curve_o_Overall_GM$Response <- 'o' 
Curve_o_Overall_YS$Response <- 'o' 


Curve_d_Overall_HM$Predictor = 'HM'
Curve_d_Overall_CV$Predictor = 'CV'
Curve_d_Overall_AL$Predictor = 'AL'
Curve_d_Overall_GM$Predictor = 'GM'
Curve_d_Overall_YS$Predictor = 'YS'

Curve_L_Overall_HM$Predictor = 'HM'
Curve_L_Overall_CV$Predictor = 'CV'
Curve_L_Overall_AL$Predictor = 'AL'
Curve_L_Overall_GM$Predictor = 'GM'
Curve_L_Overall_YS$Predictor = 'YS'

Curve_o_Overall_HM$Predictor = 'HM'
Curve_o_Overall_CV$Predictor = 'CV'
Curve_o_Overall_AL$Predictor = 'AL'
Curve_o_Overall_GM$Predictor = 'GM'
Curve_o_Overall_YS$Predictor = 'YS'


bind_rows(Curve_d_Overall_HM,
          Curve_d_Overall_CV,
          Curve_d_Overall_AL,
          Curve_d_Overall_GM,
          Curve_d_Overall_YS,
          Curve_L_Overall_HM,
          Curve_L_Overall_CV,
          Curve_L_Overall_AL,
          Curve_L_Overall_GM,
          Curve_L_Overall_YS,
          Curve_o_Overall_HM,
          Curve_o_Overall_CV,
          Curve_o_Overall_AL,
          Curve_o_Overall_GM ,
          Curve_o_Overall_YS) %>%
  filter(variable=='b_Intercept') -> AllCurveCoefs
```

```{r}
AllCurveCoefs
write_csv(AllCurveCoefs,'../ModelSummaries/AllCurveCoefs.csv')

```

## Rough Plot
```{r}
AllCurveCoefs%>%
  ggplot( aes( x = Predictor))+
  geom_pointrange(aes(y = mean, ymin = q5, ymax = q95))+
  scale_colour_viridis_c()+
  geom_hline(yintercept =0)+
  facet_wrap(Response~., ncol=1)+
  ggtitle('Overall (Cross-BCR) Turnover Curve Predictors')+
  coord_flip()
```


# Session Info

```{r}
sessionInfo()
```
